---
title: "X_gillSpiracleAnalysis"
output: html_document
---

# Load libraries

```{r}
# Load tidyverse
library(tidyverse)

# Load broom
library(broom)

# Load patchwork for plotting
library(patchwork)
```

# Load data

```{r}
# Load csv
rayData <- read.csv("Data/Data_Tidy/allMuseumRayData.csv")
```

# Split data by propulsion method

```{r}
# Caudal propulsion
caudalSpecies <- rayData %>%
  filter(PropulsionMethod == "Caudal Propulsion")

# Pectoral oscillation
oscSpecies <- rayData %>%
  filter(PropulsionMethod == "Pectoral Oscillation")

# Pectoral undulation
undSpecies <- rayData %>%
  filter(PropulsionMethod == "Pectoral Undulation")
```

# Drop NAs and species with < 4 individuals

```{r}
# Caudal propulsion
caudalSpecies <- caudalSpecies %>%
  # Drop rows with NAs in GSH and SPL
  drop_na(SpiracleLength, GSavg) %>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()

# Pectoral oscillation
oscSpecies <- oscSpecies %>%
  # Drop rows with NAs in GSH and SPL
  drop_na(SpiracleLength, GSavg) %>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()

# Pectoral undulation
undSpecies <- undSpecies %>%
  # Drop rows with NAs in GSH and SPL
  drop_na(SpiracleLength, GSavg)%>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()
```

# Analyze data

Caudal Propulsion

```{r}
# Log x (GSH), y (SPL), and z (body size)
logCaudal <- caudalSpecies %>%
  mutate(logGSH = log10(GSavg),
         logSPL = log10(SpiracleLength),
         logTL = log10(TotalLength_CM)) %>%
  # Center x (GSH) and z (body size)
  mutate(scaleSPL = scale(logSPL, center = TRUE, scale = FALSE),
         scaleTL = scale(logTL, center = TRUE, scale = FALSE))

# Model SPL ~ GSH * Species * TL
caudalModel <- lm(logGSH ~  scaleSPL * Genus_species,
                  data = logCaudal)

summary(caudalModel)
```

Pectoral Oscillation

```{r}
# Log x (SPL), y (GSH), and z (body size)
logOsc <- oscSpecies %>%
  mutate(logGSH = log10(GSavg),
         logSPL = log10(SpiracleLength),
         logDW = log10(DiscWidth_CM)) %>%
  # Center x (SPL) and z (body size)
  mutate(scaleSPL = scale(logSPL, center = TRUE, scale = FALSE),
         scaleDW = scale(logDW, center = TRUE, scale = FALSE))

# Model GSH ~ SPL
oscModel <- lm(logGSH ~  scaleSPL * Genus_species, data = logOsc)

summary(oscModel)
```

Pectoral Undulation

```{r}
# Log x (GSH), y (SPL), and z (body size)
logUnd <- undSpecies %>%
  mutate(logGSH = log10(GSavg),
         logSPL = log10(SpiracleLength),
         logDW = log10(DiscWidth_CM)) %>%
  # Center x (SPL) and z (body size)
  mutate(scaleSPL = scale(logSPL, center = TRUE, scale = FALSE),
         scaleDW = scale(logDW, center = TRUE, scale = FALSE))

# Model GSH ~ SPL
undModel <- lm(logGSH ~  scaleSPL * Genus_species, data = logUnd)

summary(undModel)
```

# Calculate confidence intervals

```{r}
# Caudal propulsion
caudalConf <- confint(caudalModel, level = 0.95)

# Pectoral oscillation
oscConf <- confint(oscModel, level = 0.95)

# Pectoral undulation
undConf <- confint(undModel, level = 0.95)
```

# Plot

# Caudal propulsion

```{r}
caudalPlot <- ggplot(data = logCaudal, aes(x = scaleSPL, y = logGSH,
                                    color = Family)) +
  geom_point() +
  scale_color_manual(values = c("Glaucostegidae" = "#130032",
                                "Pristidae" = "#492268",
                                "Rhinidae" = "#5f2c88",
                                "Rhinobatidae" = "#a26acf",
                                "Trygonorrhinidae" = "#bc94dc",
                                "Zanobatidae" = "#e3d1f0",
                                "Narcinidae" = "#de6b00",
                                "Narkidae" = "#d5a702",
                                "Torpedinidae" = "#ffdd00")) +
  facet_wrap(~ Genus_species, scales = "free") +
  labs(x = "Spiracle length (mm)",
       y = "Gill slit height (mm)") +
  theme_classic() +
  theme()

caudalPlot

ggsave("Results/Figures/caudalGSH_SPL.png", caudalPlot,
       width = 16, height = 9)
```

# Pectoral oscillation

```{r}
oscPlot <- ggplot(data = logOsc, aes(x = scaleSPL, y = logGSH,
                                    color = Family)) +
  geom_point() +
  scale_color_manual(values = c("Myliobatidae" = "#C4203A",
                                "Rhinopteridae" = "#ED909F")) +
  facet_wrap(~ Genus_species, scales = "free") +
  labs(x = "Spiracle length (mm)",
       y = "Gill slit height (mm)") +
  theme_classic() +
  theme()

oscPlot

ggsave("Results/Figures/oscGSH_SPL.png", oscPlot,
       width = 16, height = 9)
```

# Pectoral undulation

```{r}
undPlot <- ggplot(data = logUnd, aes(x = scaleSPL, y = logGSH,
                                    color = Family)) +
  geom_point() +
  scale_color_manual(values = c(# Rajiformes
                                "Anacanthobatidae" = "#023e8a",
                                "Arhynchobatidae" = "#0077b6",
                                "Gurgesiellidae" = "#00b4d8",
                                "Rajidae" = "#ade8f4",
                                # Myliobatiformes
                                "Dasyatidae" = "#570e1a",
                                "Gymnuridae" = "#761323",
                                "Hexatrygonidae" = "#8a1729",
                                "Plesiobatidae" = "#DF3853",
                                "Potamotrygonidae" = "#E66479",
                                "Urolophidae" = "#F4BCC5",
                                "Urotrygonidae" = "#f9dce0")) +
  facet_wrap(~ Genus_species, scales = "free") +
  labs(x = "Spiracle length (mm)",
       y = "Gill slit height (mm)") +
  theme_classic() +
  theme()

undPlot

ggsave("Results/Figures/undGSH_SPL.png", undPlot,
       width = 16, height = 9)
```