---
title: "X_landmarksCircularity"
output: html_document
---

## Purpose

Analyze landmarks of ray disc morphology from tpsDig.

```{r setup, load libraries}
# Load tidyverse
library(tidyverse)

# Load geomorph for working with tpsDig output
library(geomorph)
```

### Step 1: Upload data csv files

Data from tpsDig is located in "Data_Raw".

```{r upload}
# Load tpsDig results
tpsData <- readland.tps("Data/Data_Raw/Outlines_RoW.TPS", 
                         specID = "imageID", 
                         readcurves = TRUE)

# # Load other name file
# fishsimple3 <- read.csv("Data_Raw/ShortSpecimenNames5.csv")
```

### Step 2: Mirror the left-side outline

Test mirroring to confirm outlines transform properly.

```{r}
# Extract a single specimen (specimen #5)
testSpecimen <- tpsData[,,5]

# Convert to data frame
spec5 <- as.data.frame(testSpecimen)
# Name columns 'x' and 'y'
names(spec5) <- c("x", "y")
# Preview first 5 columns of spec5
head(spec5)

# Plot original landmarked side
plot(spec5$x, spec5$y,
     asp = 1,
     pch = 16,
     xlab = "x",
     ylab = "y")

# Get x-coordinate of snout tip (landmark #1)
axis <- spec5$x[1]

# Create mirrored side
spec5mirror <- data.frame(
  x = 2 * axis - spec5$x,
  y = spec5$y
)

# Plot mirrored side
plot(spec5mirror$x, spec5mirror$y,
     asp = 1,
     pch = 16,
     xlab = "x",
     ylab = "y")

# Reverse the rows
spec5mirror <- spec5mirror[nrow(spec5mirror):1, ]

# Create full outline
outline <- rbind(spec5, spec5mirror)

# Plot the outline
plot(outline$x, outline$y,
     type = "l",
     asp = 1,
     lwd = 2)
```

Create a function to be able to loop through all rays.

```{r}
# Create function 
mirrorOutline <- function(specimen){
  # Convert matrix to a data frame
  lhs <- as.data.frame(specimen)
  # Name the columns 'x' and 'y'
  names(lhs) <- c("x", "y")
  # Define the midline using the snout tip (landmark 1)
  axis <- lhs$x[1]
  # Mirror the left side across the midline
  rhs <- data.frame(
    x = 2 * axis - lhs$x,
    y = lhs$y
  )
  # Reverse mirrored landmarks so the outline traces continuously
  rhs <- rhs[nrow(rhs):1, ]
  # Combine left and right sides
  outline <- rbind(lhs, rhs)
  # Return the outline
  return(outline)
}
```

Test function.

```{r}
# Test the function on specimen 5
testFunction <- mirrorOutline(tpsData[,,5])

# Plot the outline
plot(testFunction$x, testFunction$y,
     type = "l",
     asp = 1,
     lwd = 2)
```

Loop through all those bad Larry's.

```{r}
# Create an empty list to store the 633 outlines
allOutlines <- vector("list", dim(tpsData)[3])

# Loop through specimens
for(i in 1:dim(tpsData)[3]) {
  
  allOutlines[[i]] <- mirrorOutline(tpsData[,,i])
  
}
```

Check a few outlines.

```{r}
plot(allOutlines[[10]]$x,
     allOutlines[[10]]$y,
     type = "l",
     asp = 1)

plot(allOutlines[[25]]$x,
     allOutlines[[25]]$y,
     type = "l",
     asp = 1)

plot(allOutlines[[150]]$x,
     allOutlines[[150]]$y,
     type = "l",
     asp = 1)

plot(allOutlines[[445]]$x,
     allOutlines[[445]]$y,
     type = "l",
     asp = 1)
```

Save the outlines.

```{r}
# Save outlines
saveRDS(allOutlines, "Data/Data_Tidy/mirroredOutlines.rds")

# Load outlines
allOutlines <- readRDS("Data/Data_Tidy/mirroredOutlines.rds")
```

### Step 3: Analyze circularity

```{r}
# Extract a single specimen (specimen #12)
testOutline <- allOutlines[[12]]

# Plot outline
plot(testOutline$x, testOutline$y,
     asp = 1,
     pch = 16,
     xlab = "x",
     ylab = "y")

# Get x and y
x <- testOutline$x
y <- testOutline$y

# Count the points (should be 70)
n <- length(x)

# Repeat the first point at the end (requirement of shoelace formula)
x2 <- c(x, x[1])
y2 <- c(y, y[1])

# Calculate area using the shoelace formula
A <- abs(sum(
  x2[1:n] * y2[2:(n+1)] -
  x2[2:(n+1)] * y2[1:n]
)) / 2

# Check the value of A
A

# Calculate the distance between each point
P <- sum(
  sqrt(diff(x2)^2 + diff(y2)^2)
)

# Check the value of P
P

# Calculate circularity
circularityTest <- 4*pi*A/P^2

circularityTest
```

Create a function to loop through all the rays.

```{r}
circularity <- function(outline) {
  
  x <- outline$x
  y <- outline$y
  
  n <- length(x)
  
  x2 <- c(x, x[1])
  y2 <- c(y, y[1])
  
  A <- abs(sum(
    x2[1:n] * y2[2:(n+1)] -
    x2[2:(n+1)] * y2[1:n]
  )) / 2
  
  P <- sum(
    sqrt(diff(x2)^2 + diff(y2)^2)
  )
  
  circ <- 4*pi*A/P^2
  
  return(circ)
}
```

Test function.

```{r}
circularityTest <- circularity(testOutline)

circularityTest
```

Loop through the rays.

```{r}
allCircularity <- numeric(length(allOutlines))

for(i in 1:length(allOutlines)) {
  allCircularity[i] <- circularity(allOutlines[[i]])
}
```

Check a few circularity values.

```{r}
allCircularity[10]

allCircularity[25]

allCircularity[150]

allCircularity[445]
```

### Step 4: Extract names and combine

```{r}
speciesNames <- tibble(
  Genus_species = dimnames(tpsData)[[3]]) %>%
  # Use mutate to remove the file path
  mutate(Genus_species = basename(Genus_species),
         # Remove the .png file extension
         Genus_species = str_remove(Genus_species, "\\.png$"),
         # Remove the image identifiers
         Genus_species = str_remove(Genus_species, "_[0-9]+$"))
```

Convert circularity results to a dataframe.

```{r}
# Convert to a data frame
circularityResults <- data.frame(Circularity = allCircularity)
```


Combine the names with the circularity results.

```{r}
rayCircularity <- bind_cols(
  speciesNames,
  circularityResults
)
```


### Step 5: Save.

Save this nonsense.

```{r}
# Save as a csv
write.csv(rayCircularity, "Data/Data_Tidy/RoW_Circularity.csv", row.names = FALSE)
```
