---
title: "X_phylogeneticAnalysis"
output: html_document
date: "2026-07-13"
---

## Purpose

To resolve taxonomic differences between data files and phylogenetic trees.

### Step 1: Load libraries

Load the libraries used.

```{r}
# Load tidyverse for sanity
library(tidyverse)

# Load phytools, ape, and geiger for working with phylogenetic trees
library(phytools)
library(ape)
library(geiger)
```

### Step 2: Load files

Load:
* Nex file 
* Ray files

```{r}
# Read the tree file
ogTrees <- read.nexus("Data/Data_Raw/PhylogeneticTrees/output.nex")

# Use read.csv to load museum summary
rayData <- read.csv("Data/Data_Tidy/allMuseumRayData.csv")

# Load taxonomic crosswalk
rayXwalk <- read.csv("Data/Data_Raw/TreeTaxonomicCrosswalk.csv")

# Load species to remove from trees
rayExclude <- read.csv("Data/Data_Raw/TreeSpeciesToExclude.csv")
```

View the current tip labels

```{r}
# Sample a single tree from prunedTrees
sampleOGTree <- sample(ogTrees, 1)[[1]]

# Get the tip labels
tip_labels <- as.data.frame(sampleOGTree$tip.label)
print(tip_labels)
```

### Step 3: Rename tree tips

Resolve name changes in the phylogenetic trees.

```{r}
# Create a function to loop through trees and adopt changes from sharkXwalk
rename_tips <- function(tree, corrections) {
  # Create map of old names to new names
  name_map <- deframe(corrections)

  # Apply the mapping
  new_labels <- ifelse(tree$tip.label %in% names(name_map),
                       name_map[tree$tip.label],
                       tree$tip.label)

  tree$tip.label <- new_labels

  # Identify duplicated names after renaming (i.e. synonyms)
  dupes <- duplicated(tree$tip.label)

  # If duplicates exist, drop ALL BUT one
  if (any(dupes)) {
    tree <- drop.tip(tree, tree$tip.label[dupes])
  }

  return(tree)
}

# Run trees through rename_tips function
cleanTrees <- lapply(ogTrees, rename_tips, rayXwalk)
# Make sure cleanTrees is a multiPhylo object
class(cleanTrees) <- "multiPhylo"

# Compare original tree tips and cleaned tree tips
# Check original trees
# Check if the *old* name is present in the old trees
any(sapply(ogTrees, function(tree) {
  "Himantura_fai" %in% tree$tip.label
}))
# Should return TRUE

# Check if the *new* name is present in the old trees
any(sapply(ogTrees, function(tree) {
  "Pateobatis_fai" %in% tree$tip.label
}))
# Should return FALSE

# Check cleaned trees
# Check if the *new* name is present in the new trees
any(sapply(cleanTrees, function(tree) {
  "Pateobatis_fai" %in% tree$tip.label
}))
# Should return TRUE

# Check if the *old* name is still in the new trees 
any(sapply(cleanTrees, function(tree) {
  "Himantura_fai" %in% tree$tip.label
}))
# Should return FALSE
```

### Step 4: Remove some species

Some species need to be excluded for various reasons.
See rayExclude for more informations.

```{r}
# Create vector of names to exclude
excludeNames <- rayExclude$Genus_species

# Remove species from trees
prunedTrees <- lapply(cleanTrees, function(tree) {
  drop.tip(tree, tip = intersect(tree$tip.label, excludeNames))
})

# Reassign class so it's recognized as a multiPhylo object
class(prunedTrees) <- "multiPhylo"

# Check if an excluded name is still in the trees
any(sapply(prunedTrees, function(tree) {
  "Myliobatis_rhombus" %in% tree$tip.label
}))
# Should return FALSE

# Second check that an excluded name is still in the trees
any(sapply(prunedTrees, function(tree) {
  "Amblyraja_badia" %in% tree$tip.label
}))
# Should return FALSE
```

### Step 5: Add newly described species as a sister to the present genus

We'll add new species within the genus without assuming a specific sister taxa.
phytools offers a handy function, add.species.to.genus().
However, this function only works on ultrametric trees

```{r}
# Set seed for reproducibility
set.seed(123)

# Sample a single tree from prunedTrees
sampleTree <- sample(prunedTrees, 1)[[1]]

# Identify which species are in data but missing from tree
# Extract tip labels from tree
treeSpecies <- sampleTree$tip.label
# Extract species from data
dataSpecies <- rayData$Genus_species
# Use setdiff to create a list of species that are missing
missingSpecies <- setdiff(dataSpecies, treeSpecies)
# View missingSpecies
missingSpecies

# Check whether the sampleTree is ultrametric or not
is.ultrametric(sampleTree)
# Should return FALSE

# Assign branch lengths using the Grafen method
sampleTree1 <- compute.brlen(sampleTree, method = "Grafen")

# Check whether the new sampleTree1 is ultrametric or not
is.ultrametric(sampleTree1)
# Should return TRUE

# For loop to add species from missingSpecies
for (sp in missingSpecies) {
  sampleTree1 <- add.species.to.genus(
    tree = sampleTree1,
    species = sp,
    # Add new species to the root of the genus (does not assume sister taxa is known)
    where = "root"
  )
}

# Confirm all data species are now in the tree
setdiff(dataSpecies, sampleTree1$tip.label)
# Should return "character(0)"
```

There are a few genera that are not monophyletic. 
add.species.to.genus() attaches new species to the most inclusive group.

Now we can apply these changes to all the trees.

```{r}
augment_trees <- function(tree, missingSpecies) {
  # Assign Grafen branch lengths
  tree <- compute.brlen(tree, method = "Grafen")
  # Add missing species
  for (sp in missingSpecies) {
    genus <- sub("_.*", "", sp)
    tree <- add.species.to.genus(
      tree    = tree,
      species = sp,
      where   = "root"
    )
  }
  tree
}

# Apply to all trees
augmentedTrees <- lapply(
  prunedTrees,
  augment_trees,
  missingSpecies = missingSpecies
)

# Reassign class so augmentedTrees is recognized as a multiPhylo object
class(augmentedTrees) <- "multiPhylo"
```

### Step 6: Sanity check trees are up to date and trim any remaining unused species

```{r}
# Set the seed for reproducibility
set.seed(123)

# Sample out a single tree
sampleTreeA <- sample(augmentedTrees, 1)[[1]]

# View which species are a mismatch between the tree and data
diffNames <- name.check(sampleTreeA, rayData, rayData$Genus_species)
# (should return a list of 440+ species in tree but not in data)

# Keep only tips that are present in the data
sampleTreeA <- drop.tip(sampleTreeA,
                        setdiff(sampleTreeA$tip.label, rayData$Genus_species))

# Check names again (should return "OK")
diffNamesCheck <- name.check(sampleTreeA, rayData, rayData$Genus_species)

# Apply dropped species to all trees
augmentedTreesTrim <- lapply(augmentedTrees, function(tr) {
  drop.tip(tr, setdiff(tr$tip.label, rayData$Genus_species))
})

# Reassign class so augmentedTreesTrim is recognized as a multiPhylo object
class(augmentedTreesTrim) <- "multiPhylo"

# Confirm all trees now match the data
all(sapply(augmentedTreesTrim, function(tr) {
  length(setdiff(rayData$Genus_species, tr$tip.label)) == 0
}))
# Should return TRUE

# Sample out a single tree
sampleTreeB <- sample(augmentedTreesTrim, 1)[[1]]

# Double-check that names match
diffNamesCheck2 <- name.check(sampleTreeB, rayData, rayData$Genus_species)
```

### Step 8: Save trimmed data file and trees

```{r}
# Use write.csv to save data frame as a csv in Data_Processed
write.csv(rayData, "Data/Data_Processed/RayDataTrimmed.csv", row.names = FALSE)

# Use write.nexus to save cleaned up trees to Data_Processed
write.nexus(augmentedTreesTrim, file = "Data/Data_Processed/PrunedTrimmedTrees.nex")
```