---
title: "X_scalingAnalysis"
output: html_document
---

# Load libraries

```{r}
# Load tidyverse
library(tidyverse)

# Load broom
library(broom)

# Load patchwork for plotting
library(patchwork)
```

# Load data

```{r}
# Load csv
rayData <- read.csv("Data/Data_Tidy/allMuseumRayData.csv")
```

# Split data by propulsion method

```{r}
# Caudal propulsion
caudalSpecies <- rayData %>%
  filter(PropulsionMethod == "Caudal Propulsion")

# Pectoral oscillation
oscSpecies <- rayData %>%
  filter(PropulsionMethod == "Pectoral Oscillation")

# Pectoral undulation
undSpecies <- rayData %>%
  filter(PropulsionMethod == "Pectoral Undulation")
```

# Calculate proportional size of spiracles and gills

```{r}
# Caudal propulsion
caudalSpecies <- caudalSpecies %>%
  # Calculate proportions
  mutate(SPL_TL = ((SpiracleLength * 10) / TotalLength_CM),
         GSH_TL = ((GSavg * 10) / TotalLength_CM)) %>%
  # Drop rows with NAs
  drop_na(SPL_TL, GSH_TL) %>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()

# Pectoral oscillation
oscSpecies <- oscSpecies %>%
  mutate(SPL_DW = ((SpiracleLength * 10) / DiscWidth_CM),
         GSH_DW = ((GSavg * 10) / DiscWidth_CM)) %>%
  drop_na(SPL_DW, GSH_DW) %>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()

# Pectoral undulation
undSpecies <- undSpecies %>%
  mutate(SPL_DW = ((SpiracleLength * 10) / DiscWidth_CM),
         GSH_DW = ((GSavg * 10) / DiscWidth_CM)) %>%
  drop_na(SPL_DW, GSH_DW)%>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()
```

# Analyze data with linear models

Caudal Propulsion

```{r}
# Log x (body size) and y (GSH and SPL)
logCaudal <- caudalSpecies %>%
  mutate(logGSH_TL = log10(GSH_TL),
         logSPL_TL = log10(SPL_TL),
         logTL = log10(TotalLength_CM))

# Model TL ~ GSH
caudalGSHmodel <- lm(logGSH_TL ~  logTL * Genus_species, data = logCaudal)
# View model summary
summary(caudalGSHmodel)
# Convert summary to a df
caudalGSHmodel_sum <- tidy(caudalGSHmodel)
# Export to csv
write.csv(caudalGSHmodel_sum, file = "Results/Tables/CaudalModelGSH.csv", row.names = FALSE)

# Model TL ~ SPL
caudalSPLmodel <- lm(logSPL_TL ~ logTL * Genus_species, data = logCaudal)
# View model summary
summary(caudalSPLmodel)
# Convert summary to a df
caudalSPLmodel_sum <- tidy(caudalSPLmodel)
# Export to csv
write.csv(caudalSPLmodel_sum, file = "Results/Tables/CaudalModelSPL.csv", row.names = FALSE)
```

Pectoral Oscillation

```{r}
# Log x (body size) and y (GSH and SPL)
logOsc <- oscSpecies %>%
  mutate(logGSH_DW = log10(GSH_DW),
         logSPL_DW = log10(SPL_DW),
         logDW = log10(DiscWidth_CM))

# Model TL ~ GSH
oscGSHmodel <- lm(logGSH_DW ~  logDW * Genus_species, data = logOsc)
# View model summary
summary(oscGSHmodel)
# Convert summary to a df
oscGSHmodel_sum <- tidy(oscGSHmodel)
# Export to csv
write.csv(oscGSHmodel_sum, file = "Results/Tables/OscillationModelGSH.csv", row.names = FALSE)

# Model TL ~ SPL
oscSPLmodel <- lm(logSPL_DW ~ logDW * Genus_species, data = logOsc)
# View model summary
summary(oscSPLmodel)
# Convert summary to a df
oscSPLmodel_sum <- tidy(oscSPLmodel)
# Export to csv
write.csv(oscSPLmodel_sum, file = "Results/Tables/OscillationModelSPL.csv", row.names = FALSE)
```

Pectoral Oscillation

```{r}
# Log x (body size) and y (GSH and SPL)
logUnd <- undSpecies %>%
  mutate(logGSH_DW = log10(GSH_DW),
         logSPL_DW = log10(SPL_DW),
         logDW = log10(DiscWidth_CM))

# Model TL ~ GSH
undGSHmodel <- lm(logGSH_DW ~  logDW * Genus_species, data = logUnd)
# View model summary
summary(undGSHmodel)
# Convert summary to a df
undGSHmodel_sum <- tidy(undGSHmodel)
# Export to csv
write.csv(undGSHmodel_sum, file = "Results/Tables/UndulationModelGSH.csv", row.names = FALSE)

# Model TL ~ SPL
undSPLmodel <- lm(logSPL_DW ~ logDW * Genus_species, data = logUnd)
# View model summary
summary(undSPLmodel)
# Convert summary to a df
undSPLmodel_sum <- tidy(undSPLmodel)
# Export to csv
write.csv(undSPLmodel_sum, file = "Results/Tables/UndulationModelSPL.csv", row.names = FALSE)
```

# Generate predictions for plotting

Caudal propulsion.

```{r}
# GSH
# Generate predicted data for smooth lines
caudalGSHpred <- expand.grid(logTL = seq(min(logCaudal$logTL), 
                                         max(logCaudal$logTL), 
                                         length.out = 100),
                             Genus_species = unique(logCaudal$Genus_species))
# Add model predicted values to data frame
caudalGSHpred$predictedGSH <- predict(caudalGSHmodel, newdata = caudalGSHpred)

# SPL
# Generate predicted data for smooth lines
caudalSPLpred <- expand.grid(logTL = seq(min(logCaudal$logTL), 
                                         max(logCaudal$logTL), 
                                         length.out = 100),
                             Genus_species = unique(logCaudal$Genus_species))
# Add model predicted values to data frame
caudalSPLpred$predictedSPL <- predict(caudalSPLmodel, newdata = caudalSPLpred)
```

Pectoral oscillation.

```{r}
# GSH
# Generate predicted data for smooth lines
oscGSHpred <- expand.grid(logDW = seq(min(logOsc$logDW), 
                                         max(logOsc$logDW), 
                                         length.out = 100),
                          Genus_species = unique(logOsc$Genus_species))
# Add model predicted values to data frame
oscGSHpred$predictedGSH <- predict(oscGSHmodel, newdata = oscGSHpred)

# SPL
# Generate predicted data for smooth lines
oscSPLpred <- expand.grid(logDW = seq(min(logOsc$logDW), 
                                         max(logOsc$logDW), 
                                         length.out = 100),
                             Genus_species = unique(logOsc$Genus_species))
# Add model predicted values to data frame
oscSPLpred$predictedSPL <- predict(oscSPLmodel, newdata = oscSPLpred)
```

Pectoral undulation.

```{r}
# GSH
# Generate predicted data for smooth lines
undGSHpred <- expand.grid(logDW = seq(min(logUnd$logDW), 
                                         max(logUnd$logDW), 
                                         length.out = 100),
                          Genus_species = unique(logUnd$Genus_species))
# Add model predicted values to data frame
undGSHpred$predictedGSH <- predict(undGSHmodel, newdata = undGSHpred)

# SPL
# Generate predicted data for smooth lines
undSPLpred <- expand.grid(logDW = seq(min(logUnd$logDW), 
                                         max(logUnd$logDW), 
                                         length.out = 100),
                             Genus_species = unique(logUnd$Genus_species))
# Add model predicted values to data frame
undSPLpred$predictedSPL <- predict(undSPLmodel, newdata = undSPLpred)
```

# Plot results

Caudal propulsion.

```{r}
# Plot data with lines from model predictions
caudalPlot <- ggplot(data = logCaudal, aes(x = logTL, y = logGSH_TL,
                                    color = Family)) +
  geom_line(data = caudalGSHpred, aes(x = logTL, y = predictedGSH, 
                                      color = Genus_species),
            linewidth = 0.5) +
  geom_point() +
  scale_color_manual(values = c("Glaucostegidae" = "#130032",
                                "Pristidae" = "#492268",
                                "Rhinidae" = "#5f2c88",
                                "Rhinobatidae" = "#a26acf",
                                "Trygonorrhinidae" = "#bc94dc",
                                "Zanobatidae" = "#e3d1f0",
                                "Narcinidae" = "#de6b00",
                                "Narkidae" = "#d5a702",
                                "Torpedinidae" = "#ffdd00")) +
  facet_wrap(~ Genus_species, scales = "free_x") +
  labs(x = "Total length (cm)",
       y = "Relative gill slit height") +
  theme_classic() +
  theme()

caudalPlot

ggsave("Results/Figures/caudalGSH_lines.png", caudalPlot,
       width = 16, height = 9)
```

Pectoral oscillation.

```{r}
# Plot data with lines from model predictions
oscPlot <- ggplot(data = logOsc, aes(x = logDW, y = logGSH_DW,
                                     color = Family)) +
  geom_line(data = oscGSHpred, aes(x = logDW, y = predictedGSH, 
                                      color = Genus_species),
            linewidth = 0.5) +
  geom_point() +
  scale_color_manual(values = c("Myliobatidae" = "#C4203A",
                                "Rhinopteridae" = "#ED909F")) +
  facet_wrap(~ Genus_species, scales = "free_x") +
  labs(x = "Disc width (cm)",
       y = "Relative gill slit height") +
  theme_classic() +
  theme()

oscPlot

ggsave("Results/Figures/oscGSH_lines.png", oscPlot,
       width = 16, height = 9)
```

Pectoral undulation.

```{r}
# Plot data with lines from model predictions
undPlot <- ggplot(data = logUnd, aes(x = logDW, y = logGSH_DW,
                                     color = Family)) +
  geom_line(data = undGSHpred, aes(x = logDW, y = predictedGSH, 
                                      color = Genus_species),
            linewidth = 0.5) +
  geom_point() +
  scale_color_manual(values = c(# Rajiformes
                                "Anacanthobatidae" = "#023e8a",
                                "Arhynchobatidae" = "#0077b6",
                                "Gurgesiellidae" = "#00b4d8",
                                "Rajidae" = "#ade8f4",
                                # Myliobatiformes
                                "Dasyatidae" = "#570e1a",
                                "Gymnuridae" = "#761323",
                                "Hexatrygonidae" = "#8a1729",
                                "Plesiobatidae" = "#DF3853",
                                "Potamotrygonidae" = "#E66479",
                                "Urolophidae" = "#F4BCC5",
                                "Urotrygonidae" = "#f9dce0")) +
  facet_wrap(~ Genus_species, scales = "free_x") +
  labs(x = "Disc width (cm)",
       y = "Relative gill slit height") +
  theme_classic() +
  theme()

undPlot

ggsave("Results/Figures/undGSH_lines.png", undPlot,
       width = 16, height = 9)
```
