---
title: "X_scalingAnalysis"
output: html_document
---

# 1. Load libraries

```{r}
# Load tidyverse
library(tidyverse)

# Load brms and tidybayes for analysis and interpretation
library(brms)
library(tidybayes)

# Load ape, geiger, and phytools for phylogenetic tree wrangling
library(ape)
library(geiger)
library(phytools)

# Load patchwork, cowplot, and scales for plotting
library(patchwork)
library(cowplot)
library(scales)
```

# 2. Load data

```{r}
# Load csv
rayData <- read.csv("Data/Data_Processed/RayDataTrimmed.csv")

# Load phylogenetic trees
rayTrees <- read.nexus("Data/Data_Processed/PrunedTrimmedTrees.nex")
```

# 3. Split data by propulsion method for ease of analysis

```{r}
# Caudal propulsion
caudalSpecies <- rayData %>%
  filter(PropulsionMethod == "Caudal Propulsion")

# Pectoral oscillation
oscSpecies <- rayData %>%
  filter(PropulsionMethod == "Pectoral Oscillation")

# Pectoral undulation
undSpecies <- rayData %>%
  filter(PropulsionMethod == "Pectoral Undulation")
```

# 4. Calculate proportional size of spiracles and gills

```{r}
# Caudal propulsion
caudalSpecies <- caudalSpecies %>%
  # Convert spiracles and gills to cm
  mutate(SPL_CM = SpiracleLength / 10,
         GSH_CM = GSavg / 10) %>%
  # Calculate proportions
  mutate(SPL_TL = SPL_CM / TotalLength_CM,
         GSH_TL = GSH_CM / TotalLength_CM) %>%
  # Drop rows with NAs in SPL or GSH
  drop_na(SPL_TL, GSH_TL) %>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()

# Pectoral oscillation
oscSpecies <- oscSpecies %>%
  # Convert spiracles and gills to cm
  mutate(SPL_CM = SpiracleLength / 10,
         GSH_CM = GSavg / 10) %>%
  # Calculate proportions
  mutate(SPL_DW = SPL_CM / DiscWidth_CM,
         GSH_DW = GSH_CM / DiscWidth_CM) %>%
  # Drop rows with NAs in SPL or GSH
  drop_na(SPL_DW, GSH_DW) %>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()

# Pectoral undulation
undSpecies <- undSpecies %>%
  # Convert spiracles and gills to cm
  mutate(SPL_CM = SpiracleLength / 10,
         GSH_CM = GSavg / 10) %>%
  # Calculate proportions
  mutate(SPL_DW = SPL_CM / DiscWidth_CM,
         GSH_DW = GSH_CM / DiscWidth_CM) %>%
  # Drop rows with NAs in SPL or GSH
  drop_na(SPL_DW, GSH_DW)%>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()
```

# 5. Prepare phylogenetic trees

```{r}
# Set the seed for reproducibility
set.seed(123)
```

Trim trees to match each division of the dataset.

Caudal species

```{r}
# Sample out a single tree
caudalTree <- sample(rayTrees, 1)[[1]]

# View which species are a mismatch between the tree and data
diffNamesCaudal <- name.check(caudalTree, caudalSpecies, caudalSpecies$Genus_species)
# (should return a list of 162 species in tree but not in data)

# Keep only tips that are present in the data
caudalTree <- drop.tip(caudalTree,
                        setdiff(caudalTree$tip.label, caudalSpecies$Genus_species))

# Check names again (should return "OK")
diffNamesCaudal <- name.check(caudalTree, caudalSpecies, caudalSpecies$Genus_species)

# Keep only species present in the tree
caudalSpecies <- caudalSpecies[caudalSpecies$Genus_species %in% caudalTree$tip.label, ]
```

Pectoral oscillators

```{r}
# Sample out a single tree
oscTree <- sample(rayTrees, 1)[[1]]

# View which species are a mismatch between the tree and data
diffNamesOsc <- name.check(oscTree, oscSpecies, oscSpecies$Genus_species)
# (should return a list of 190 species in tree but not in data)

# Keep only tips that are present in the data
oscTree <- drop.tip(oscTree,
                    setdiff(oscTree$tip.label, oscSpecies$Genus_species))

# Check names again (should return "OK")
diffNamesosc <- name.check(oscTree, oscSpecies, oscSpecies$Genus_species)

# Keep only species present in the tree
oscSpecies <- oscSpecies[oscSpecies$Genus_species %in% oscTree$tip.label, ]
```

Pectoral undulators

```{r}
# Sample out a single tree
undTree <- sample(rayTrees, 1)[[1]]

# View which species are a mismatch between the tree and data
diffNamesUnd <- name.check(undTree, undSpecies, undSpecies$Genus_species)
# (should return a list of 141 species in tree but not in data)

# Keep only tips that are present in the data
undTree <- drop.tip(undTree,
                    setdiff(undTree$tip.label, undSpecies$Genus_species))

# Check names again (should return "OK")
diffNamesUnd <- name.check(undTree, undSpecies, undSpecies$Genus_species)

# Keep only species present in the tree
undSpecies <- undSpecies[undSpecies$Genus_species %in% undTree$tip.label, ]
```

# 6. Analyze data with brms

## 6.1 Caudal Propulsion

Prepare data by logging x and y, and centering x

```{r}
# Log x (body size) and y (GSH and SPL)
logCaudal <- caudalSpecies %>%
  mutate(logGSH_TL = log10(GSH_TL),
         logSPL_TL = log10(SPL_TL),
         logTL = log10(TotalLength_CM))
```

Create and run brms models

### 6.1.1 SPL

```{r}
# Create variance covariance matrix
caudalMatrix <- ape::vcv(caudalTree)

# Scale TL (predictor (x))
caudalScaled <- logCaudal %>%
  # "Scale" by centering only (since testing isometry)
  mutate(scaleTL = scale(logTL, center = TRUE, scale = FALSE))

# Build and run model
caudalModel_SPL <- brm(logSPL_TL ~ scaleTL +
                     (1 + scaleTL | gr(Genus_species, cov = caudalMatrix)),
          data = caudalScaled,
          data2 = list(caudalMatrix = caudalMatrix),
          family = gaussian,
          warmup = 4000, iter = 8000,
          cores = 2, control = list(adapt_delta = 0.95),
          save_pars = save_pars(all = TRUE))

summary(caudalModel_SPL)

# Save brms object
saveRDS(caudalModel_SPL, "Results/brmsOutputs/caudalModel_SPL.rds")
```

```{r}
# Optional: load brms object if revisiting script
caudalModel_SPL <- readRDS("Results/brmsOutputs/caudalModel_SPL.rds")
```

Extract model outputs

```{r}
caudalSPL_slopes <- caudalModel_SPL %>%
  # Get "global" posterior draws
  spread_draws(b_scaleTL,
    # Get species level posterior draws
    r_Genus_species[Genus_species, term]) %>%
  # Filter for slopes (remove Intercept)
  filter(term == "scaleTL") %>%
  # Calculate species' "true" slope (global slope + slope relative to "global" slope)
  mutate(slope = b_scaleTL + r_Genus_species)

# Summarize by species
sum_caudalSPL <- caudalSPL_slopes %>%
  median_qi(slope, .width = 0.95) %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "),
         # Flag species that deviate from expectations
         significant = (.lower >=0 | .upper <= 0))
```

Create coefficient plot

```{r}
caudalSPLcoef <- ggplot(sum_caudalSPL,
       aes(x = slope, y = reorder(Genus_species, slope), 
           color = significant)) +
  geom_vline(xintercept = 0, color = "grey50") +
  geom_errorbar(aes(xmin = .lower, xmax = .upper),
                width = 0) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = NULL,
        y = NULL) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 8, face = "italic"),
        legend.position = "none")

ggsave("Results/Figures/caudalSPL_coef.png", caudalSPLcoef,
       width = 8, height = 10)
```

### 6.1.2 GSH

```{r}
# Build and run model
caudalModel_GSH <- brm(logGSH_TL ~ scaleTL +
                     (1 + scaleTL | gr(Genus_species, cov = caudalMatrix)),
          data = caudalScaled,
          data2 = list(caudalMatrix = caudalMatrix),
          family = gaussian,
          warmup = 4000, iter = 8000,
          cores = 2, control = list(adapt_delta = 0.95),
          save_pars = save_pars(all = TRUE))

summary(caudalModel_GSH)

# Save brms object
saveRDS(caudalModel_GSH, "Results/brmsOutputs/caudalModel_GSH.rds")
```

```{r}
# Optional: load brms object if revisiting script
caudalModel_GSH <- readRDS("Results/brmsOutputs/caudalModel_GSH.rds")
```

Extract model outputs

```{r}
caudalGSH_slopes <- caudalModel_GSH %>%
  # Get "global" posterior draws
  spread_draws(b_scaleTL,
    # Get species level posterior draws
    r_Genus_species[Genus_species, term]) %>%
  # Filter for slopes (remove Intercept)
  filter(term == "scaleTL") %>%
  # Calculate species' "true" slope (global slope + slope relative to "global" slope)
  mutate(slope = b_scaleTL + r_Genus_species)

# Summarize by species
sum_caudalGSH <- caudalGSH_slopes %>%
  median_qi(slope, .width = 0.95) %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "),
         # Flag species that deviate from expectations
         significant = (.lower >=0 | .upper <= 0))
```

Create coefficient plot

```{r}
caudalGSHcoef <- ggplot(sum_caudalGSH,
       aes(x = slope, y = reorder(Genus_species, slope),
           color = significant)) +
  geom_vline(xintercept = 0, color = "grey50") +
  geom_errorbar(aes(xmin = .lower, xmax = .upper),
                width = 0) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = NULL,
       y = NULL) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 8, face = "italic"),
        legend.position = "none")

ggsave("Results/Figures/caudalGSH_coef.png", caudalGSHcoef,
       width = 8, height = 10)
```

## 6.2 Pectoral Oscillation

Prepare data by logging x and y, and centering x

```{r}
# Log x (body size) and y (GSH and SPL)
logOsc <- oscSpecies %>%
  mutate(logGSH_DW = log10(GSH_DW),
         logSPL_DW = log10(SPL_DW),
         logDW = log10(DiscWidth_CM))
```

Create and run brms models

### 6.2.1 SPL

```{r}
# Create variance covariance matrix
oscMatrix <- ape::vcv(oscTree)

# Scale DW (predictor (x))
oscScaled <- logOsc %>%
  # "Scale" by centering only (since testing isometry)
  mutate(scaleDW = scale(logDW, center = TRUE, scale = FALSE))

# Build and run model
oscModel_SPL <- brm(logSPL_DW ~ scaleDW +
                     (1 + scaleDW | gr(Genus_species, cov = oscMatrix)),
          data = oscScaled,
          data2 = list(oscMatrix = oscMatrix),
          family = gaussian,
          warmup = 4000, iter = 8000,
          cores = 2, control = list(adapt_delta = 0.95),
          save_pars = save_pars(all = TRUE))

summary(oscModel_SPL)

# Save brms object
saveRDS(oscModel_SPL, "Results/brmsOutputs/oscModel_SPL.rds")
```

```{r}
# Optional: load brms object if revisiting script
oscModel_SPL <- readRDS("Results/brmsOutputs/oscModel_SPL.rds")
```

Extract model outputs

```{r}
oscSPL_slopes <- oscModel_SPL %>%
  # Get "global" posterior draws
  spread_draws(b_scaleDW,
    # Get species level posterior draws
    r_Genus_species[Genus_species, term]) %>%
  # Filter for slopes (remove Intercept)
  filter(term == "scaleDW") %>%
  # Calculate species' "true" slope (global slope + slope relative to "global" slope)
  mutate(slope = b_scaleDW + r_Genus_species)

# Summarize by species
sum_oscSPL <- oscSPL_slopes %>%
  median_qi(slope, .width = 0.95) %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "),
         # Flag species that deviate from expectations
         significant = (.lower >=0 | .upper <= 0))
```

Plot 

```{r}
oscSPLcoef <- ggplot(sum_oscSPL,
                     aes(x = slope, y = reorder(Genus_species, slope),
                         color = significant)) +
  geom_vline(xintercept = 0, color = "grey50") +
  geom_errorbar(aes(xmin = .lower, xmax = .upper),
                width = 0) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = NULL,
        y = NULL) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 8, face = "italic"),
        legend.position = "none")

ggsave("Results/Figures/oscSPL_coef.png", oscSPLcoef,
       width = 8, height = 10)
```

### 6.2.2 GSH

```{r}
# Build and run model
oscModel_GSH <- brm(logGSH_DW ~ scaleDW +
                     (1 + scaleDW | gr(Genus_species, cov = oscMatrix)),
          data = oscScaled,
          data2 = list(oscMatrix = oscMatrix),
          family = gaussian,
          warmup = 4000, iter = 8000,
          cores = 2, control = list(adapt_delta = 0.95),
          save_pars = save_pars(all = TRUE))

summary(oscModel_GSH)

# Save brms object
saveRDS(oscModel_GSH, "Results/brmsOutputs/oscModel_GSH.rds")
```

```{r}
# Optional: load brms object if revisiting script
oscModel_GSH <- readRDS("Results/brmsOutputs/oscModel_GSH.rds")
```

Extract model outputs

```{r}
oscGSH_slopes <- oscModel_GSH %>%
  # Get "global" posterior draws
  spread_draws(b_scaleDW,
    # Get species level posterior draws
    r_Genus_species[Genus_species, term]) %>%
  # Filter for slopes (remove Intercept)
  filter(term == "scaleDW") %>%
  # Calculate species' "true" slope (global slope + slope relative to "global" slope)
  mutate(slope = b_scaleDW + r_Genus_species)

# Summarize by species
sum_oscGSH <- oscGSH_slopes %>%
  median_qi(slope, .width = 0.95) %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "),
         # Flag species that deviate from expectations
         significant = (.lower >=0 | .upper <= 0))
```

Create coefficient plot

```{r}
oscGSHcoef <- ggplot(sum_oscGSH,
                     aes(x = slope, y = reorder(Genus_species, slope),
           color = significant)) +
  geom_vline(xintercept = 0, color = "grey50") +
  geom_errorbar(aes(xmin = .lower, xmax = .upper),
                width = 0) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = NULL,
       y = NULL) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 8, face = "italic"),
        legend.position = "none")

ggsave("Results/Figures/oscGSH_coef.png", oscGSHcoef,
       width = 8, height = 10)
```

## 6.3 Pectoral Undulation

Prepare data by logging x and y, and centering x

```{r}
# Log x (body size) and y (GSH and SPL)
logUnd <- undSpecies %>%
  mutate(logGSH_DW = log10(GSH_DW),
         logSPL_DW = log10(SPL_DW),
         logDW = log10(DiscWidth_CM))
```

Create and run brms models

### 6.3.1 SPL

```{r}
# Create variance covariance matrix
undMatrix <- ape::vcv(undTree)

# Scale DW (predictor (x))
undScaled <- logUnd %>%
  # "Scale" by centering only (since testing isometry)
  mutate(scaleDW = scale(logDW, center = TRUE, scale = FALSE))

# Build and run model
undModel_SPL <- brm(logSPL_DW ~ scaleDW +
                     (1 + scaleDW | gr(Genus_species, cov = undMatrix)),
          data = undScaled,
          data2 = list(undMatrix = undMatrix),
          family = gaussian,
          warmup = 4000, iter = 8000,
          cores = 2, control = list(adapt_delta = 0.95),
          save_pars = save_pars(all = TRUE))

summary(undModel_SPL)

# Save brms object
saveRDS(undModel_SPL, "Results/brmsOutputs/undModel_SPL.rds")
```

```{r}
# Optional: load brms object if revisiting script
undModel_SPL <- readRDS("Results/brmsOutputs/undModel_SPL.rds")
```

Extract model outputs

```{r}
undSPL_slopes <- undModel_SPL %>%
  # Get "global" posterior draws
  spread_draws(b_scaleDW,
    # Get species level posterior draws
    r_Genus_species[Genus_species, term]) %>%
  # Filter for slopes (remove Intercept)
  filter(term == "scaleDW") %>%
  # Calculate species' "true" slope (global slope + slope relative to "global" slope)
  mutate(slope = b_scaleDW + r_Genus_species)

# Summarize by species
sum_undSPL <- undSPL_slopes %>%
  median_qi(slope, .width = 0.95) %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "),
         # Flag species that deviate from expectations
         significant = (.lower >=0 | .upper <= 0))
```

Create coefficient plot 

```{r}
undSPLcoef <- ggplot(sum_undSPL,
                     aes(x = slope, y = reorder(Genus_species, slope),
                         color = significant)) +
  geom_vline(xintercept = 0, color = "grey50") +
  geom_errorbar(aes(xmin = .lower, xmax = .upper),
                width = 0) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = NULL,
        y = NULL) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 8, face = "italic"),
        legend.position = "none")

ggsave("Results/Figures/undSPL_coef.png", undSPLcoef,
       width = 8, height = 10)
```

### 6.3.2 GSH

```{r}
# Build and run model
undModel_GSH <- brm(logGSH_DW ~ scaleDW +
                     (1 + scaleDW | gr(Genus_species, cov = undMatrix)),
          data = undScaled,
          data2 = list(undMatrix = undMatrix),
          family = gaussian,
          warmup = 4000, iter = 8000,
          cores = 2, control = list(adapt_delta = 0.95),
          save_pars = save_pars(all = TRUE))

summary(undModel_GSH)

# Save brms object
saveRDS(undModel_GSH, "Results/brmsOutputs/undModel_GSH.rds")
```


```{r}
# Optional: load brms object if revisiting script
undModel_GSH <- readRDS("Results/brmsOutputs/undModel_GSH.rds")
```

Extract model outputs

```{r}
undGSH_slopes <- undModel_GSH %>%
  # Get "global" posterior draws
  spread_draws(b_scaleDW,
    # Get species level posterior draws
    r_Genus_species[Genus_species, term]) %>%
  # Filter for slopes (remove Intercept)
  filter(term == "scaleDW") %>%
  # Calculate species' "true" slope (global slope + slope relative to "global" slope)
  mutate(slope = b_scaleDW + r_Genus_species)

# Summarize by species
sum_undGSH <- undGSH_slopes %>%
  median_qi(slope, .width = 0.95) %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "),
         # Flag species that deviate from expectations
         significant = (.lower >=0 | .upper <= 0))
```

Create coefficient plot

```{r}
undGSHcoef <- ggplot(sum_undGSH,
                     aes(x = slope, y = reorder(Genus_species, slope),
           color = significant)) +
  geom_vline(xintercept = 0, color = "grey50") +
  geom_errorbar(aes(xmin = .lower, xmax = .upper),
                width = 0) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = NULL,
       y = NULL) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 8, face = "italic"),
        legend.position = "none")

ggsave("Results/Figures/undGSH_coef.png", undGSHcoef,
       width = 8, height = 10)
```

# 7. Plot species data with model predictions



```{r}

```







###############################################################################

# Old things?

```{r}
# # Model TL ~ GSH
# caudalGSHmodel <- lm(logGSH_TL ~  logTL * Genus_species, data = logCaudal)
# # View model summary
# summary(caudalGSHmodel)
# # Convert summary to a df
# caudalGSHmodel_sum <- tidy(caudalGSHmodel)
# # Export to csv
# write.csv(caudalGSHmodel_sum, file = "Results/Tables/CaudalModelGSH.csv", 
#           row.names = FALSE)
# 
# # Model TL ~ SPL
# caudalSPLmodel <- lm(logSPL_TL ~ logTL * Genus_species, data = logCaudal)
# # View model summary
# summary(caudalSPLmodel)
# # Convert summary to a df
# caudalSPLmodel_sum <- tidy(caudalSPLmodel)
# # Export to csv
# write.csv(caudalSPLmodel_sum, file = "Results/Tables/CaudalModelSPL.csv", 
#           row.names = FALSE)
# ```
# 
# ```{r}
# # GSH
# # Extract coefficients table
# caudalGSH_coef <- summary(caudalGSHmodel)$coefficients
# # "Attach" a significance status to each species
# caudalGSH_status <- data.frame(Genus_species = unique(logCaudal$Genus_species)) %>%
#   rowwise() %>%
#   mutate(
#     # Create column to place p-values for each species
#     p_val = {
#       row_name <- paste0("logTL:Genus_species", Genus_species)
#       if (row_name %in% rownames(caudalGSH_coef)) {
#         # Get the p-value
#         caudalGSH_coef[row_name, "Pr(>|t|)"]
#       } else {
#         # p-value for "reference" species
#         caudalGSH_coef["logTL", "Pr(>|t|)"]
#       }
#     },
#     # Classify significance based on p-value of 0.05
#     Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
#   ungroup()
# 
# # SPL
# # Extract coefficients table
# caudalSPL_coef <- summary(caudalSPLmodel)$coefficients
# # "Attach" a significance status to each species
# caudalSPL_status <- data.frame(Genus_species = unique(logCaudal$Genus_species)) %>%
#   rowwise() %>%
#   mutate(
#     # Create column to place p-values for each species
#     p_val = {
#       row_name <- paste0("logTL:Genus_species", Genus_species)
#       if (row_name %in% rownames(caudalSPL_coef)) {
#         # Get the p-value
#         caudalSPL_coef[row_name, "Pr(>|t|)"]
#       } else {
#         # p-value for "reference" species
#         caudalSPL_coef["logTL", "Pr(>|t|)"]
#       }
#     },
#     # Classify significance based on p-value of 0.05
#     Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
#   ungroup()
# ```
# 
# Pectoral Oscillation
# 
# ```{r}
# # Log x (body size) and y (GSH and SPL)
# logOsc <- oscSpecies %>%
#   mutate(logGSH_DW = log10(GSH_DW),
#          logSPL_DW = log10(SPL_DW),
#          logDW = log10(DiscWidth_CM))
# 
# # Model TL ~ GSH
# oscGSHmodel <- lm(logGSH_DW ~  logDW * Genus_species, data = logOsc)
# # View model summary
# summary(oscGSHmodel)
# # Convert summary to a df
# oscGSHmodel_sum <- tidy(oscGSHmodel)
# # Export to csv
# write.csv(oscGSHmodel_sum, file = "Results/Tables/OscillationModelGSH.csv", 
#           row.names = FALSE)
# 
# # Model TL ~ SPL
# oscSPLmodel <- lm(logSPL_DW ~ logDW * Genus_species, data = logOsc)
# # View model summary
# summary(oscSPLmodel)
# # Convert summary to a df
# oscSPLmodel_sum <- tidy(oscSPLmodel)
# # Export to csv
# write.csv(oscSPLmodel_sum, file = "Results/Tables/OscillationModelSPL.csv", 
#           row.names = FALSE)
# ```
# 
# ```{r}
# # GSH
# # Extract coefficients table
# oscGSH_coef <- summary(oscGSHmodel)$coefficients
# # "Attach" a significance status to each species
# oscGSH_status <- data.frame(Genus_species = unique(logOsc$Genus_species)) %>%
#   rowwise() %>%
#   mutate(
#     # Create column to place p-values for each species
#     p_val = {
#       row_name <- paste0("logDW:Genus_species", Genus_species)
#       if (row_name %in% rownames(oscGSH_coef)) {
#         # Get the p-value
#         oscGSH_coef[row_name, "Pr(>|t|)"]
#       } else {
#         # p-value for "reference" species
#         oscGSH_coef["logDW", "Pr(>|t|)"]
#       }
#     },
#     # Classify significance based on p-value of 0.05
#     Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
#   ungroup()
# 
# # SPL
# # Extract coefficients table
# oscSPL_coef <- summary(oscSPLmodel)$coefficients
# # "Attach" a significance status to each species
# oscSPL_status <- data.frame(Genus_species = unique(logOsc$Genus_species)) %>%
#   rowwise() %>%
#   mutate(
#     # Create column to place p-values for each species
#     p_val = {
#       row_name <- paste0("logDW:Genus_species", Genus_species)
#       if (row_name %in% rownames(oscSPL_coef)) {
#         # Get the p-value
#         oscSPL_coef[row_name, "Pr(>|t|)"]
#       } else {
#         # p-value for "reference" species
#         oscSPL_coef["logDW", "Pr(>|t|)"]
#       }
#     },
#     # Classify significance based on p-value of 0.05
#     Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
#   ungroup()
# ```
# 
# Pectoral Undulation
# 
# ```{r}
# # Log x (body size) and y (GSH and SPL)
# logUnd <- undSpecies %>%
#   mutate(logGSH_DW = log10(GSH_DW),
#          logSPL_DW = log10(SPL_DW),
#          logDW = log10(DiscWidth_CM))
# 
# # Model TL ~ GSH
# undGSHmodel <- lm(logGSH_DW ~  logDW * Genus_species, data = logUnd)
# # View model summary
# summary(undGSHmodel)
# # Convert summary to a df
# undGSHmodel_sum <- tidy(undGSHmodel)
# # Export to csv
# write.csv(undGSHmodel_sum, file = "Results/Tables/UndulationModelGSH.csv", 
#           row.names = FALSE)
# 
# # Model TL ~ SPL
# undSPLmodel <- lm(logSPL_DW ~ logDW * Genus_species, data = logUnd)
# # View model summary
# summary(undSPLmodel)
# # Convert summary to a df
# undSPLmodel_sum <- tidy(undSPLmodel)
# # Export to csv
# write.csv(undSPLmodel_sum, file = "Results/Tables/UndulationModelSPL.csv", 
#           row.names = FALSE)
# ```
# 
# ```{r}
# # GSH
# # Extract coefficients table
# undGSH_coef <- summary(undGSHmodel)$coefficients
# # "Attach" a significance status to each species
# undGSH_status <- data.frame(Genus_species = unique(logUnd$Genus_species)) %>%
#   rowwise() %>%
#   mutate(
#     # Create column to place p-values for each species
#     p_val = {
#       row_name <- paste0("logDW:Genus_species", Genus_species)
#       if (row_name %in% rownames(undGSH_coef)) {
#         # Get the p-value
#         undGSH_coef[row_name, "Pr(>|t|)"]
#       } else {
#         # p-value for "reference" species
#         undGSH_coef["logDW", "Pr(>|t|)"]
#       }
#     },
#     # Classify significance based on p-value of 0.05
#     Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
#   ungroup()
# 
# # SPL
# # Extract coefficients table
# undSPL_coef <- summary(undSPLmodel)$coefficients
# # "Attach" a significance status to each species
# undSPL_status <- data.frame(Genus_species = unique(logUnd$Genus_species)) %>%
#   rowwise() %>%
#   mutate(
#     # Create column to place p-values for each species
#     p_val = {
#       row_name <- paste0("logDW:Genus_species", Genus_species)
#       if (row_name %in% rownames(undSPL_coef)) {
#         # Get the p-value
#         undSPL_coef[row_name, "Pr(>|t|)"]
#       } else {
#         # p-value for "reference" species
#         undSPL_coef["logDW", "Pr(>|t|)"]
#       }
#     },
#     # Classify significance based on p-value of 0.05
#     Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
#   ungroup()
# ```
# 
# # Generate predictions for plotting (instead of geom_smooth from ggplot)
# 
# Caudal propulsion.
# 
# ```{r}
# # GSH
# # Generate predicted data, grouping by species
# caudalGSHpred <- logCaudal %>%
#   group_by(Genus_species) %>%
#   reframe(logTL = seq(min(logTL), max(logTL), length.out = 100))
# # Add model predicted values to data frame
# caudalGSHpred$predictedGSH <- predict(caudalGSHmodel, newdata = caudalGSHpred)
# 
# # SPL
# # Generate predicted data for smooth lines
# caudalSPLpred <- logCaudal %>%
#   group_by(Genus_species) %>%
#   reframe(logTL = seq(min(logTL), max(logTL), length.out = 100))
# # Add model predicted values to data frame
# caudalSPLpred$predictedSPL <- predict(caudalSPLmodel, newdata = caudalSPLpred)
# ```
# 
# Join the significance status to data
# 
# ```{r}
# # Actual data
# # GSH
# logCaudalGSH <- logCaudal %>%
#   left_join(caudalGSH_status, by = "Genus_species")
# # SPL
# logCaudalSPL <- logCaudal %>%
#   left_join(caudalSPL_status, by = "Genus_species")
# 
# # Prediction data
# # GSH
# caudalGSHpred <- caudalGSHpred %>%
#   left_join(caudalGSH_status, by = "Genus_species")
# # SPL
# caudalSPLpred <- caudalSPLpred %>%
#   left_join(caudalSPL_status, by = "Genus_species")
# ```
# 
# Pectoral oscillation.
# 
# ```{r}
# # GSH
# # Generate predicted data for smooth lines
# oscGSHpred <- logOsc %>%
#   group_by(Genus_species) %>%
#   reframe(logDW = seq(min(logDW), max(logDW), length.out = 100))
# # Add model predicted values to data frame
# oscGSHpred$predictedGSH <- predict(oscGSHmodel, newdata = oscGSHpred)
# 
# # SPL
# # Generate predicted data for smooth lines
# oscSPLpred <- logOsc %>%
#   group_by(Genus_species) %>%
#   reframe(logDW = seq(min(logDW), max(logDW), length.out = 100))
# # Add model predicted values to data frame
# oscSPLpred$predictedSPL <- predict(oscSPLmodel, newdata = oscSPLpred)
# ```
# 
# Join the significance status to data
# 
# ```{r}
# # Actual data
# # GSH
# logOscGSH <- logOsc %>%
#   left_join(oscGSH_status, by = "Genus_species")
# # SPL
# logOscSPL <- logOsc %>%
#   left_join(oscSPL_status, by = "Genus_species")
# 
# # Predictions
# # GSH
# oscGSHpred <- oscGSHpred %>%
#   left_join(oscGSH_status, by = "Genus_species")
# # SPL
# oscSPLpred <- oscSPLpred %>%
#   left_join(oscSPL_status, by = "Genus_species")
# ```
# 
# Pectoral undulation.
# 
# ```{r}
# # GSH
# # Generate predicted data for smooth lines
# undGSHpred <- logUnd %>%
#   group_by(Genus_species) %>%
#   reframe(logDW = seq(min(logDW), max(logDW), length.out = 100))
# # Add model predicted values to data frame
# undGSHpred$predictedGSH <- predict(undGSHmodel, newdata = undGSHpred)
# 
# # SPL
# # Generate predicted data for smooth lines
# undSPLpred <- logUnd %>%
#   group_by(Genus_species) %>%
#   reframe(logDW = seq(min(logDW), max(logDW), length.out = 100))
# # Add model predicted values to data frame
# undSPLpred$predictedSPL <- predict(undSPLmodel, newdata = undSPLpred)
# ```
# 
# Join the significance status to data
# 
# ```{r}
# # Actual data
# # GSH
# logUndGSH <- logUnd %>%
#   left_join(undGSH_status, by = "Genus_species")
# # SPL
# logUndSPL <- logUnd %>%
#   left_join(undSPL_status, by = "Genus_species")
# 
# # Predictions
# # GSH
# undGSHpred <- undGSHpred %>%
#   left_join(undGSH_status, by = "Genus_species")
# # SPL
# undSPLpred <- undSPLpred %>%
#   left_join(undSPL_status, by = "Genus_species")
# ```
# 
# # Plot results
# 
# Caudal propulsion.
# 
# ```{r}
# # Replace _ with " "
# # Actual data
# logCaudalGSH <- logCaudalGSH %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# 
# logCaudalSPL <- logCaudalSPL %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# 
# # GSH
# # Predictions
# caudalGSHpred <- caudalGSHpred %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# 
# # SPL
# # Predictions
# caudalSPLpred <- caudalSPLpred %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# ```
# 
# ```{r}
# # Plot GSH data with lines from model predictions
# caudalGSHplot <- ggplot(data = logCaudalGSH, aes(x = logTL, y = logGSH_TL)) +
#   geom_line(data = caudalGSHpred,
#             aes(x = logTL, y = predictedGSH, group = Genus_species, 
#                 color = Significance),
#             linewidth = 0.5) +
#   geom_point(data = logCaudalGSH, aes(group = Genus_species, color = Significance)) +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   facet_wrap(~ Genus_species, scales = "free_x", ncol = 4) +
#   scale_x_continuous(labels = function(x) round(10^x)) +
#   scale_y_continuous(labels = function(y) round(10^y, 2)) +
#   labs(x = "Total length (cm)",
#        y = "Relative gill slit height") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8),
#         # Set facet strip aesthetics
#         strip.text = element_text(face = "italic", size = 8),
#         strip.background = element_blank(),
#         # Set legend aesthetics
#         legend.direction = "horizontal",
#         legend.title.position = "top", 
#         legend.title = element_text(hjust = 0.5))
# 
# caudalGSHplot
# 
# # Extract legend
# legend <- get_legend(caudalGSHplot)
# legend <- ggdraw(legend)
# 
# # Replot without legend
# caudalGSHplot <- caudalGSHplot +
#   theme(legend.position = "none")
# # Confirm legend does not plot
# caudalGSHplot
# 
# # Plot SPL data with lines from model predictions
# caudalSPLplot <- ggplot(data = logCaudalSPL, aes(x = logTL, y = logSPL_TL)) +
#   geom_line(data = caudalSPLpred,
#             aes(x = logTL, y = predictedSPL, group = Genus_species, 
#                 color = Significance),
#             linewidth = 0.5) +
#   geom_point(data = logCaudalSPL, aes(group = Genus_species, color = Significance)) +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   facet_wrap(~ Genus_species, scales = "free_x",
#              ncol = 4) +
#   scale_x_continuous(labels = function(x) round(10^x)) +
#   scale_y_continuous(labels = function(y) round(10^y, 2),
#                      limits = c(-2.1, -1.2)) +
#   labs(x = "Total length (cm)",
#        y = "Relative spiracle length") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8),
#         # Set facet strip aesthetics
#         strip.text = element_text(face = "italic", size = 8),
#         strip.background = element_blank(),
#         legend.position = "none")
# 
# caudalSPLplot
# ```
# 
# ```{r}
# # Combined plots
# caudal <- (caudalGSHplot + caudalSPLplot) /
#   legend +
#   plot_layout(heights = c(1, 0.05))
# 
# caudal
# 
# ggsave("Results/Figures/caudalIsometry.png", caudal,
#        width = 16, height = 10)
# ```
# 
# Pectoral oscillation.
# 
# ```{r}
# # Replace _ with " "
# # Actual data
# logOscGSH <- logOscGSH %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# 
# logOscSPL <- logOscSPL %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# 
# # GSH
# # Predictions
# oscGSHpred <- oscGSHpred %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# 
# # SPL
# # Predictions
# oscSPLpred <- oscSPLpred %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# ```
# 
# ```{r}
# # Plot GSH data with lines from model predictions
# oscGSHplot <- ggplot(data = logOscGSH, aes(x = logDW, y = logGSH_DW)) +
#   geom_line(data = oscGSHpred,
#             aes(x = logDW, y = predictedGSH, group = Genus_species, 
#                 color = Significance),
#             linewidth = 0.5) +
#   geom_point(data = logOscGSH, aes(group = Genus_species, color = Significance)) +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   facet_wrap(~ Genus_species, scales = "free_x",
#              ncol = 2) +
#   scale_x_continuous(labels = function(x) round(10^x)) +
#   scale_y_continuous(labels = function(y) round(10^y, 2)) +
#   labs(x = "Disc Width (cm)",
#        y = "Relative gill slit height") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8),
#         # Set facet strip aesthetics
#         strip.text = element_text(face = "italic", size = 8),
#         strip.background = element_blank(),
#         legend.position = "none")
# 
# oscGSHplot
# 
# # Plot SPL data with lines from model predictions
# oscSPLplot <- ggplot(data = logOscSPL, aes(x = logDW, y = logSPL_DW)) +
#   geom_line(data = oscSPLpred,
#             aes(x = logDW, y = predictedSPL, group = Genus_species, 
#                 color = Significance),
#             linewidth = 0.5) +
#   geom_point(data = logOscSPL, aes(group = Genus_species, color = Significance)) +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   facet_wrap(~ Genus_species, scales = "free_x",
#              ncol = 2) +
#   scale_x_continuous(labels = function(x) round(10^x)) +
#   scale_y_continuous(labels = function(y) round(10^y, 2)) +
#   labs(x = "Disc Width (cm)",
#        y = "Relative spiracle length") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8),
#         # Set facet strip aesthetics
#         strip.text = element_text(face = "italic", size = 8),
#         strip.background = element_blank(),
#         legend.position = "none")
# 
# oscSPLplot
# ```
# 
# ```{r}
# # Combined plots
# osc <- (oscGSHplot + oscSPLplot) /
#   legend +
#   plot_layout(heights = c(1, 0.05))
# 
# osc
# 
# ggsave("Results/Figures/oscIsometry.png", osc,
#        width = 16, height = 10)
# ```
# 
# Pectoral undulation.
# 
# ```{r}
# # Replace _ with " "
# # Actual data
# logUndGSH <- logUndGSH %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# 
# logUndSPL <- logUndSPL %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# 
# # GSH
# # Predictions
# undGSHpred <- undGSHpred %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# 
# # SPL
# # Predictions
# undSPLpred <- undSPLpred %>%
#   mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
# ```
# 
# ```{r}
# # Plot GSH data with lines from model predictions
# undGSHplot <- ggplot(data = logUndGSH, aes(x = logDW, y = logGSH_DW)) +
#   geom_line(data = undGSHpred,
#             aes(x = logDW, y = predictedGSH, group = Genus_species, 
#                 color = Significance),
#             linewidth = 0.5) +
#   geom_point(data = logUndGSH, aes(group = Genus_species, color = Significance)) +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   facet_wrap(~ Genus_species, scales = "free_x",
#              ncol = 5) +
#   scale_x_continuous(labels = function(x) round(10^x)) +
#   scale_y_continuous(labels = function(y) round(10^y, 2)) +
#   labs(x = "Disc Width (cm)",
#        y = "Relative gill slit height") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8),
#         # Set facet strip aesthetics
#         strip.text = element_text(face = "italic", size = 8),
#         strip.background = element_blank(),
#         legend.position = "none")
# 
# undGSHplot
# 
# # Plot SPL data with lines from model predictions
# undSPLplot <- ggplot(data = logUndSPL, aes(x = logDW, y = logSPL_DW)) +
#   geom_line(data = undSPLpred,
#             aes(x = logDW, y = predictedSPL, group = Genus_species, 
#                 color = Significance),
#             linewidth = 0.5) +
#   geom_point(data = logUndSPL, aes(group = Genus_species, color = Significance)) +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   facet_wrap(~ Genus_species, scales = "free_x",
#              ncol = 5) +
#   scale_x_continuous(labels = function(x) round(10^x)) +
#   scale_y_continuous(labels = function(y) round(10^y, 2)) +
#   labs(x = "Disc width (cm)",
#        y = "Relative spiracle length") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8),
#         # Set facet strip aesthetics
#         strip.text = element_text(face = "italic", size = 8),
#         strip.background = element_blank(),
#         legend.position = "none")
# 
# undSPLplot
# ```
# 
# ```{r}
# # Combined plots
# und <- (undGSHplot + undSPLplot) /
#   legend +
#   plot_layout(heights = c(1, 0.03))
# 
# und
# 
# ggsave("Results/Figures/undIsometry.png", und,
#        width = 16, height = 10)
# ```
# 
# # Supplementary Analysis
# 
# 
# ```{r}
# # Caudal
# caudalSPLp <- logCaudalSPL %>%
#   count(Genus_species, p_val, Significance)
# 
# caudalSPL <- ggplot(data = caudalSPLp, aes(x = n, y = p_val, color = Significance)) +
#   geom_point() +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   labs(x = "Number of individuals",
#        y = "p-value",
#        title = "Caudal propulsion, SPL") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8))
# 
# caudalSPL
# 
# caudalGSHp <- logCaudalGSH %>%
#   count(Genus_species, p_val, Significance)
# 
# caudalGSH <- ggplot(data = caudalGSHp, aes(x = n, y = p_val, color = Significance)) +
#   geom_point() +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   labs(x = "Number of individuals",
#        y = "p-value",
#        title = "Caudal propulsion, GSH") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8))
# 
# caudalGSH
# 
# # Oscillation
# oscSPLp <- logOscSPL %>%
#   count(Genus_species, p_val, Significance)
# 
# oscSPL <- ggplot(data = oscSPLp, aes(x = n, y = p_val, color = Significance)) +
#   geom_point() +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   labs(x = "Number of individuals",
#        y = "p-value",
#        title = "Pectoral Oscillation, SPL") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8))
# 
# oscSPL
# 
# oscGSHp <- logOscGSH %>%
#   count(Genus_species, p_val, Significance)
# 
# oscGSH <- ggplot(data = oscGSHp, aes(x = n, y = p_val, color = Significance)) +
#   geom_point() +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   labs(x = "Number of individuals",
#        y = "p-value",
#        title = "Pectoral Oscillation, GSH") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8))
# 
# oscGSH
# 
# # Undulation
# undSPLp <- logUndSPL %>%
#   count(Genus_species, p_val, Significance)
# 
# undSPL <- ggplot(data = undSPLp, aes(x = n, y = p_val, color = Significance)) +
#   geom_point() +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   labs(x = "Number of individuals",
#        y = "p-value",
#        title = "Pectoral Undulation, SPL") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8))
# 
# undSPL
# 
# undGSHp <- logUndGSH %>%
#   count(Genus_species, p_val, Significance)
# 
# undGSH <- ggplot(data = undGSHp, aes(x = n, y = p_val, color = Significance)) +
#   geom_point() +
#   scale_color_manual(values = c("Significant" = "royalblue", 
#                                 "Not Significant" = "grey60")) +
#   labs(x = "Number of individuals",
#        y = "p-value",
#        title = "Pectoral Undulation, GSH") +
#   theme_classic() +
#   theme(axis.text = element_text(size = 8))
# 
# undGSH
```
