---
title: "X_scalingAnalysis"
output: html_document
---

# Load libraries

```{r}
# Load tidyverse
library(tidyverse)

# Load patchwork
library(patchwork)
```

# Load data

```{r}
# Load csv
rayData <- read.csv("Data/Data_Tidy/allMuseumRayData.csv")
```

# Preprocess data for clean plotting later

```{r}
rayData <- rayData %>%
  # Replace _ in Genus_species with a space
  mutate(Genus_species = gsub("_", " ", Genus_species))
```

# Split data by propulsion method

```{r}
# Caudal propulsion
caudalSpecies <- rayData %>%
  filter(PropulsionMethod == "Caudal Propulsion")

# Pectoral oscillation
oscSpecies <- rayData %>%
  filter(PropulsionMethod == "Pectoral Oscillation")

# Pectoral undulation
undSpecies <- rayData %>%
  filter(PropulsionMethod == "Pectoral Undulation")
```

# Calculate proportional size of spiracles and gills

```{r}
# Caudal propulsion
caudalSpecies <- caudalSpecies %>%
  # Calculate proportions
  mutate(SPL_TL = ((SpiracleLength * 10) / TotalLength_CM),
         GSH_TL = ((GSavg * 10) / TotalLength_CM)) %>%
  # Drop rows with NAs
  drop_na(SPL_TL, GSH_TL) %>%
  # Remove species with less than 3 individuals
  group_by(Genus_species) %>%
  filter(n() > 2) %>%
  ungroup()

# Pectoral oscillation
oscSpecies <- oscSpecies %>%
  mutate(SPL_DW = ((SpiracleLength * 10) / DiscWidth_CM),
         GSH_DW = ((GSavg * 10) / DiscWidth_CM)) %>%
  drop_na(SPL_DW, GSH_DW) %>%
  # Remove species with less than 3 individuals
  group_by(Genus_species) %>%
  filter(n() > 2) %>%
  ungroup()

# Pectoral undulation
undSpecies <- undSpecies %>%
  mutate(SPL_DW = ((SpiracleLength * 10) / DiscWidth_CM),
         GSH_DW = ((GSavg * 10) / DiscWidth_CM)) %>%
  drop_na(SPL_DW, GSH_DW)%>%
  # Remove species with less than 3 individuals
  group_by(Genus_species) %>%
  filter(n() > 2) %>%
  ungroup()
```

# Create some subdivided data frames for ease of visualization

Caudal propulsion - split by Order

```{r}
# Rhinopristiformes
Rhinopristiformes <- caudalSpecies %>%
  filter(Order == "Rhinopristiformes")

# Torpediniformes
Torpediniformes <- caudalSpecies %>%
  filter(Order == "Torpediniformes")
```

Pectoral oscillation - no split.

Pectoral undulation - split by Order.

```{r}
# Myliobatiformes
Myliobatiformes <- undSpecies %>%
  filter(Order == "Myliobatiformes")

# Rajiformes
Rajiformes <- undSpecies %>%
  filter(Order == "Rajiformes")
```

# Linear models

```{r}
# lm?
```

# Plot

Caudal propulsion plots.

```{r}
# Rhinopristiformes
# GSH
rhinoGSHPlot <- ggplot(Rhinopristiformes, aes(x = TotalLength_CM, y = GSH_TL,
                                           color = Family)) +
  geom_point() +
  scale_color_manual(guide = guide_legend(nrow = 1),
                     values = c("Glaucostegidae" = "#130032",
                                "Pristidae" = "#492268",
                                "Rhinidae" = "#5f2c88",
                                "Rhinobatidae" = "#a26acf",
                                "Trygonorrhinidae" = "#bc94dc",
                                "Zanobatidae" = "#e3d1f0")) +
  facet_wrap(~ Genus_species,
             scales = "free_x",
             ncol = 3) +
  labs(x = "Total length (cm)",
       y = "Relative gill slit height",
       title = "Rhinopristiformes") +
  theme_classic() +
  theme(strip.text = element_text(size = 9, face = "italic"),
        plot.title = element_text(size = 12, hjust = 0.5),
        legend.position = "none",
        axis.title.x = element_blank())

rhinoGSHPlot

# SPH
rhinoSPLplot <- ggplot(Rhinopristiformes, aes(x = TotalLength_CM, y = SPL_TL,
                                           color = Family)) +
  geom_point() +
  scale_color_manual(guide = guide_legend(nrow = 1),
                     values = c("Glaucostegidae" = "#130032",
                                "Pristidae" = "#492268",
                                "Rhinidae" = "#5f2c88",
                                "Rhinobatidae" = "#a26acf",
                                "Trygonorrhinidae" = "#bc94dc",
                                "Zanobatidae" = "#e3d1f0")) +
  facet_wrap(~ Genus_species,
             scales = "free_x",
             ncol = 3) +
  labs(x = "Total length (cm)",
       y = "Relative spiracle length") +
  theme_classic() +
  theme(strip.text = element_text(size = 9, face = "italic"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        legend.position = "bottom",
        legend.direction = "horizontal")

rhinoSPLplot

# Torpediniformes
# GSH
torpedoGSHPlot <- ggplot(Torpediniformes, aes(x = TotalLength_CM, y = GSH_TL,
                                              color = Family)) +
  geom_point() +
  scale_color_manual(guide = guide_legend(nrow = 1),
                     values = c("Narcinidae" = "#de6b00",
                                "Narkidae" = "#d5a702",
                                "Torpedinidae" = "#ffdd00")) +
  facet_wrap(~ Genus_species,
             scales = "free_x",
             ncol = 3) +
  labs(x = "Total length (cm)",
       y = "Relative gill slit height",
       title = "Torpediniformes") +
  theme_classic() +
  theme(strip.text = element_text(size = 9, face = "italic"),
        plot.title = element_text(size = 12, hjust = 0.5),
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

torpedoGSHPlot

# SPH
torpedoSPLplot <- ggplot(Torpediniformes, aes(x = TotalLength_CM, y = SPL_TL,
                                              color = Family)) +
  geom_point() +
  scale_color_manual(guide = guide_legend(nrow = 1),
                     values = c("Narcinidae" = "#de6b00",
                                "Narkidae" = "#d5a702",
                                "Torpedinidae" = "#ffdd00")) +
  facet_wrap(~ Genus_species,
              scales = "free_x",
             ncol = 3) +
  labs(x = "Total length (cm)",
       y = "Relative spiracle length") +
  theme_classic() +
  theme(strip.text = element_text(size = 9, face = "italic"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        legend.position = "bottom",
        legend.direction = "horizontal",
        axis.title.y = element_blank())

torpedoSPLplot
```

Pectoral oscillation plots.

```{r}
# GSH
oscGSHplot <- ggplot(oscSpecies, aes(x = DiscWidth_CM, y = GSH_DW,
                                  color = Family)) +
  geom_point() +
  scale_color_manual(guide = guide_legend(nrow = 1),
                     values = c("Myliobatidae" = "#C4203A",
                                "Rhinopteridae" = "#ED909F")) +
  facet_wrap(~ Genus_species, 
             scales = "free_x") +
  labs(x = "Disc width (cm)",
       y = "Relative gill slit height") +
  theme_classic() +
  theme(strip.text = element_text(size = 9, face = "italic"),
        legend.position = "none",
        axis.title.x = element_blank())

oscGSHplot

# SPL
oscSPLplot <- ggplot(oscSpecies, aes(x = DiscWidth_CM, y = SPL_DW,
                                  color = Family)) +
  geom_point() +
  scale_color_manual(guide = guide_legend(nrow = 1),
                     values = c("Myliobatidae" = "#C4203A",
                                "Rhinopteridae" = "#ED909F")) +
  facet_wrap(~ Genus_species, 
             scales = "free_x") +
  labs(x = "Disc width (cm)",
       y = "Relative spiracle length") +
  theme_classic() +
  theme(strip.text = element_text(size = 9, face = "italic"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        legend.position = "bottom",
        legend.direction = "horizontal")

oscSPLplot
```

Pectoral undulation plots.

```{r}
# Myliobatiformes
# GSH
mylioGSHPlot <- ggplot(Myliobatiformes, aes(x = DiscWidth_CM, y = GSH_DW,
                                           color = Family)) +
  geom_point() +
  scale_color_manual(guide = guide_legend(nrow = 2),
                     values = c("Dasyatidae" = "#570e1a",
                                "Gymnuridae" = "#761323",
                                "Hexatrygonidae" = "#8a1729",
                                "Plesiobatidae" = "#DF3853",
                                "Potamotrygonidae" = "#E66479",
                                "Urolophidae" = "#F4BCC5",
                                "Urotrygonidae" = "#f9dce0")) +
  facet_wrap(~ Genus_species,
             scales = "free_x",
             ncol = 4) +
  labs(x = "Disc width (cm)",
       y = "Relative gill slit height",
       title = "Myliobatiformes") +
  theme_classic() +
  theme(strip.text = element_text(size = 9, face = "italic"),
        plot.title = element_text(size = 12, hjust = 0.5),
        legend.position = "none",
        axis.title.x = element_blank())

mylioGSHPlot

# SPH
mylioSPLplot <- ggplot(Myliobatiformes, aes(x = DiscWidth_CM, y = GSH_DW,
                                           color = Family)) +
  geom_point() +
  scale_color_manual(guide = guide_legend(nrow = 2),
                     values = c("Dasyatidae" = "#570e1a",
                                "Gymnuridae" = "#761323",
                                "Hexatrygonidae" = "#8a1729",
                                "Plesiobatidae" = "#DF3853",
                                "Potamotrygonidae" = "#E66479",
                                "Urolophidae" = "#F4BCC5",
                                "Urotrygonidae" = "#f9dce0")) +
  facet_wrap(~ Genus_species,
             scales = "free_x",
             ncol = 4) +
  labs(x = "Disc width (cm)",
       y = "Relative spiracle length") +
  theme_classic() +
  theme(strip.text = element_text(size = 9, face = "italic"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        legend.position = "bottom",
        legend.direction = "horizontal")

mylioSPLplot

# Rajiformes
# GSH
rajiGSHPlot <- ggplot(Rajiformes, aes(x = DiscWidth_CM, y = GSH_DW,
                                              color = Family)) +
  geom_point() +
  scale_color_manual(guide = guide_legend(nrow = 2),
                     values = c("Anacanthobatidae" = "#023e8a",
                                "Arhynchobatidae" = "#0077b6",
                                "Gurgesiellidae" = "#00b4d8",
                                "Rajidae" = "#ade8f4")) +
  facet_wrap(~ Genus_species,
             scales = "free_x",
             ncol = 4) +
  labs(x = "Disc width (cm)",
       y = "Relative gill slit height",
       title = "Rajiformes") +
  theme_classic() +
  theme(strip.text = element_text(size = 9, face = "italic"),
        plot.title = element_text(size = 12, hjust = 0.5),
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

rajiGSHPlot

# SPH
rajiSPLplot <- ggplot(Rajiformes, aes(x = DiscWidth_CM, y = GSH_DW,
                                              color = Family)) +
  geom_point() +
  scale_color_manual(guide = guide_legend(nrow = 2),
                     values = c("Anacanthobatidae" = "#023e8a",
                                "Arhynchobatidae" = "#0077b6",
                                "Gurgesiellidae" = "#00b4d8",
                                "Rajidae" = "#ade8f4")) +
  facet_wrap(~ Genus_species,
              scales = "free_x",
             ncol = 4) +
  labs(x = "Disc width (cm)",
       y = "Relative spiracle length") +
  theme_classic() +
  theme(strip.text = element_text(size = 9, face = "italic"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        legend.position = "bottom",
        legend.direction = "horizontal",
        axis.title.y = element_blank())

rajiSPLplot
```

# Combine plots using patchwork.

```{r}
caudalPlot <- 
  # Top panel
  (rhinoGSHPlot + plot_spacer() + torpedoGSHPlot +
     # Set widths of each plot
     plot_layout(widths = c(1, 0.05, 1))) / 
  # Spacer
  plot_spacer() /
  # Bottom panel
  (rhinoSPLplot + plot_spacer() + torpedoSPLplot +
     # Set widths of each plot
     plot_layout(widths = c(1, 0.05, 1))) +
  # Set heights of each plot
  plot_layout(heights = c(1, 0.05, 1))

caudalPlot
```

```{r}
oscillationPlot <- 
  oscGSHplot / plot_spacer() / oscSPLplot +
  plot_layout(heights = c(1, 0.05, 1))

oscillationPlot
```

```{r}
undulationPlot <- 
  # Top panel
  (mylioGSHPlot + plot_spacer() + rajiGSHPlot +
     # Set widths of each plot
     plot_layout(widths = c(1, 0.05, 1))) / 
  # Spacer
  plot_spacer() /
  # Bottom panel
  (mylioSPLplot + plot_spacer() + rajiSPLplot +
     # Set widths of each plot
     plot_layout(widths = c(1, 0.05, 1))) +
  # Set heights of each plot
  plot_layout(heights = c(1, 0.05, 1))

undulationPlot
```

# Save combined plots.

```{r}
# Caudal propulsion plot
ggsave("Results/Figures/caudalPropulsionAllometry.png", caudalPlot,
       width = 12, height = 20)

# Pectoral oscillation plot
ggsave("Results/Figures/pectoralOscillationAllometry.png", oscillationPlot,
       width = 8, height = 10)

# Pectoral undulation plot
ggsave("Results/Figures/pectoralUndulationAllometry.png", undulationPlot,
       width = 12, height = 20)
```

