---
title: "X_scalingAnalysis"
output: html_document
---

# Load libraries

```{r}
# Load tidyverse
library(tidyverse)

# Load broom
library(broom)

# Load patchwork for plotting
library(patchwork)
```

# Load data

```{r}
# Load csv
rayData <- read.csv("Data/Data_Tidy/allMuseumRayData.csv")
```

# Split data by propulsion method

```{r}
# Caudal propulsion
caudalSpecies <- rayData %>%
  filter(PropulsionMethod == "Caudal Propulsion")

# Pectoral oscillation
oscSpecies <- rayData %>%
  filter(PropulsionMethod == "Pectoral Oscillation")

# Pectoral undulation
undSpecies <- rayData %>%
  filter(PropulsionMethod == "Pectoral Undulation")
```

# Calculate proportional size of spiracles and gills

```{r}
# Caudal propulsion
caudalSpecies <- caudalSpecies %>%
  # Calculate proportions
  mutate(SPL_TL = ((SpiracleLength * 10) / TotalLength_CM),
         GSH_TL = ((GSavg * 10) / TotalLength_CM)) %>%
  # Drop rows with NAs in SPL or GSH
  drop_na(SPL_TL, GSH_TL) %>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()

# Pectoral oscillation
oscSpecies <- oscSpecies %>%
  mutate(SPL_DW = ((SpiracleLength * 10) / DiscWidth_CM),
         GSH_DW = ((GSavg * 10) / DiscWidth_CM)) %>%
  # Drop rows with NAs in SPL or GSH
  drop_na(SPL_DW, GSH_DW) %>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()

# Pectoral undulation
undSpecies <- undSpecies %>%
  mutate(SPL_DW = ((SpiracleLength * 10) / DiscWidth_CM),
         GSH_DW = ((GSavg * 10) / DiscWidth_CM)) %>%
  # Drop rows with NAs in SPL or GSH
  drop_na(SPL_DW, GSH_DW)%>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()
```

# Analyze data with linear models

Caudal Propulsion

```{r}
# Log x (body size) and y (GSH and SPL)
logCaudal <- caudalSpecies %>%
  mutate(logGSH_TL = log10(GSH_TL),
         logSPL_TL = log10(SPL_TL),
         logTL = log10(TotalLength_CM))

# Model TL ~ GSH
caudalGSHmodel <- lm(logGSH_TL ~  logTL * Genus_species, data = logCaudal)
# View model summary
summary(caudalGSHmodel)
# Convert summary to a df
caudalGSHmodel_sum <- tidy(caudalGSHmodel)
# Export to csv
write.csv(caudalGSHmodel_sum, file = "Results/Tables/CaudalModelGSH.csv", 
          row.names = FALSE)

# Model TL ~ SPL
caudalSPLmodel <- lm(logSPL_TL ~ logTL * Genus_species, data = logCaudal)
# View model summary
summary(caudalSPLmodel)
# Convert summary to a df
caudalSPLmodel_sum <- tidy(caudalSPLmodel)
# Export to csv
write.csv(caudalSPLmodel_sum, file = "Results/Tables/CaudalModelSPL.csv", 
          row.names = FALSE)
```

```{r}
# GSH
# Extract coefficients table
caudalGSH_coef <- summary(caudalGSHmodel)$coefficients
# "Attach" a significance status to each species
caudalGSH_status <- data.frame(Genus_species = unique(logCaudal$Genus_species)) %>%
  rowwise() %>%
  mutate(
    # Create column to place p-values for each species
    p_val = {
      row_name <- paste0("logTL:Genus_species", Genus_species)
      if (row_name %in% rownames(caudalGSH_coef)) {
        # Get the p-value
        caudalGSH_coef[row_name, "Pr(>|t|)"]
      } else {
        # p-value for "reference" species
        caudalGSH_coef["logTL", "Pr(>|t|)"]
      }
    },
    # Classify significance based on p-value of 0.05
    Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
  ungroup()

# SPL
# Extract coefficients table
caudalSPL_coef <- summary(caudalSPLmodel)$coefficients
# "Attach" a significance status to each species
caudalSPL_status <- data.frame(Genus_species = unique(logCaudal$Genus_species)) %>%
  rowwise() %>%
  mutate(
    # Create column to place p-values for each species
    p_val = {
      row_name <- paste0("logTL:Genus_species", Genus_species)
      if (row_name %in% rownames(caudalSPL_coef)) {
        # Get the p-value
        caudalSPL_coef[row_name, "Pr(>|t|)"]
      } else {
        # p-value for "reference" species
        caudalSPL_coef["logTL", "Pr(>|t|)"]
      }
    },
    # Classify significance based on p-value of 0.05
    Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
  ungroup()
```

Pectoral Oscillation

```{r}
# Log x (body size) and y (GSH and SPL)
logOsc <- oscSpecies %>%
  mutate(logGSH_DW = log10(GSH_DW),
         logSPL_DW = log10(SPL_DW),
         logDW = log10(DiscWidth_CM))

# Model TL ~ GSH
oscGSHmodel <- lm(logGSH_DW ~  logDW * Genus_species, data = logOsc)
# View model summary
summary(oscGSHmodel)
# Convert summary to a df
oscGSHmodel_sum <- tidy(oscGSHmodel)
# Export to csv
write.csv(oscGSHmodel_sum, file = "Results/Tables/OscillationModelGSH.csv", 
          row.names = FALSE)

# Model TL ~ SPL
oscSPLmodel <- lm(logSPL_DW ~ logDW * Genus_species, data = logOsc)
# View model summary
summary(oscSPLmodel)
# Convert summary to a df
oscSPLmodel_sum <- tidy(oscSPLmodel)
# Export to csv
write.csv(oscSPLmodel_sum, file = "Results/Tables/OscillationModelSPL.csv", 
          row.names = FALSE)
```

```{r}
# GSH
# Extract coefficients table
oscGSH_coef <- summary(oscGSHmodel)$coefficients
# "Attach" a significance status to each species
oscGSH_status <- data.frame(Genus_species = unique(logOsc$Genus_species)) %>%
  rowwise() %>%
  mutate(
    # Create column to place p-values for each species
    p_val = {
      row_name <- paste0("logDW:Genus_species", Genus_species)
      if (row_name %in% rownames(oscGSH_coef)) {
        # Get the p-value
        oscGSH_coef[row_name, "Pr(>|t|)"]
      } else {
        # p-value for "reference" species
        oscGSH_coef["logDW", "Pr(>|t|)"]
      }
    },
    # Classify significance based on p-value of 0.05
    Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
  ungroup()

# SPL
# Extract coefficients table
oscSPL_coef <- summary(oscSPLmodel)$coefficients
# "Attach" a significance status to each species
oscSPL_status <- data.frame(Genus_species = unique(logOsc$Genus_species)) %>%
  rowwise() %>%
  mutate(
    # Create column to place p-values for each species
    p_val = {
      row_name <- paste0("logDW:Genus_species", Genus_species)
      if (row_name %in% rownames(oscSPL_coef)) {
        # Get the p-value
        oscSPL_coef[row_name, "Pr(>|t|)"]
      } else {
        # p-value for "reference" species
        oscSPL_coef["logDW", "Pr(>|t|)"]
      }
    },
    # Classify significance based on p-value of 0.05
    Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
  ungroup()
```

Pectoral Undulation

```{r}
# Log x (body size) and y (GSH and SPL)
logUnd <- undSpecies %>%
  mutate(logGSH_DW = log10(GSH_DW),
         logSPL_DW = log10(SPL_DW),
         logDW = log10(DiscWidth_CM))

# Model TL ~ GSH
undGSHmodel <- lm(logGSH_DW ~  logDW * Genus_species, data = logUnd)
# View model summary
summary(undGSHmodel)
# Convert summary to a df
undGSHmodel_sum <- tidy(undGSHmodel)
# Export to csv
write.csv(undGSHmodel_sum, file = "Results/Tables/UndulationModelGSH.csv", 
          row.names = FALSE)

# Model TL ~ SPL
undSPLmodel <- lm(logSPL_DW ~ logDW * Genus_species, data = logUnd)
# View model summary
summary(undSPLmodel)
# Convert summary to a df
undSPLmodel_sum <- tidy(undSPLmodel)
# Export to csv
write.csv(undSPLmodel_sum, file = "Results/Tables/UndulationModelSPL.csv", 
          row.names = FALSE)
```

```{r}
# GSH
# Extract coefficients table
undGSH_coef <- summary(undGSHmodel)$coefficients
# "Attach" a significance status to each species
undGSH_status <- data.frame(Genus_species = unique(logUnd$Genus_species)) %>%
  rowwise() %>%
  mutate(
    # Create column to place p-values for each species
    p_val = {
      row_name <- paste0("logDW:Genus_species", Genus_species)
      if (row_name %in% rownames(undGSH_coef)) {
        # Get the p-value
        undGSH_coef[row_name, "Pr(>|t|)"]
      } else {
        # p-value for "reference" species
        undGSH_coef["logDW", "Pr(>|t|)"]
      }
    },
    # Classify significance based on p-value of 0.05
    Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
  ungroup()

# SPL
# Extract coefficients table
undSPL_coef <- summary(undSPLmodel)$coefficients
# "Attach" a significance status to each species
undSPL_status <- data.frame(Genus_species = unique(logUnd$Genus_species)) %>%
  rowwise() %>%
  mutate(
    # Create column to place p-values for each species
    p_val = {
      row_name <- paste0("logDW:Genus_species", Genus_species)
      if (row_name %in% rownames(undSPL_coef)) {
        # Get the p-value
        undSPL_coef[row_name, "Pr(>|t|)"]
      } else {
        # p-value for "reference" species
        undSPL_coef["logDW", "Pr(>|t|)"]
      }
    },
    # Classify significance based on p-value of 0.05
    Significance = if_else(p_val < 0.05, "Significant", "Not Significant")) %>%
  ungroup()
```

# Generate predictions for plotting (instead of geom_smooth from ggplot)

Caudal propulsion.

```{r}
# GSH
# Generate predicted data, grouping by species
caudalGSHpred <- logCaudal %>%
  group_by(Genus_species) %>%
  reframe(logTL = seq(min(logTL), max(logTL), length.out = 100))
# Add model predicted values to data frame
caudalGSHpred$predictedGSH <- predict(caudalGSHmodel, newdata = caudalGSHpred)

# SPL
# Generate predicted data for smooth lines
caudalSPLpred <- logCaudal %>%
  group_by(Genus_species) %>%
  reframe(logTL = seq(min(logTL), max(logTL), length.out = 100))
# Add model predicted values to data frame
caudalSPLpred$predictedSPL <- predict(caudalSPLmodel, newdata = caudalSPLpred)
```

Join the significance status to data

```{r}
# Actual data
# GSH
logCaudalGSH <- logCaudal %>%
  left_join(caudalGSH_status, by = "Genus_species")
# SPL
logCaudalSPL <- logCaudal %>%
  left_join(caudalSPL_status, by = "Genus_species")

# Prediction data
# GSH
caudalGSHpred <- caudalGSHpred %>%
  left_join(caudalGSH_status, by = "Genus_species")
# SPL
caudalSPLpred <- caudalSPLpred %>%
  left_join(caudalSPL_status, by = "Genus_species")
```

Pectoral oscillation.

```{r}
# GSH
# Generate predicted data for smooth lines
oscGSHpred <- logOsc %>%
  group_by(Genus_species) %>%
  reframe(logDW = seq(min(logDW), max(logDW), length.out = 100))
# Add model predicted values to data frame
oscGSHpred$predictedGSH <- predict(oscGSHmodel, newdata = oscGSHpred)

# SPL
# Generate predicted data for smooth lines
oscSPLpred <- logOsc %>%
  group_by(Genus_species) %>%
  reframe(logDW = seq(min(logDW), max(logDW), length.out = 100))
# Add model predicted values to data frame
oscSPLpred$predictedSPL <- predict(oscSPLmodel, newdata = oscSPLpred)
```

Join the significance status to data

```{r}
# Actual data
# GSH
logOscGSH <- logOsc %>%
  left_join(oscGSH_status, by = "Genus_species")
# SPL
logOscSPL <- logOsc %>%
  left_join(oscSPL_status, by = "Genus_species")

# Predictions
# GSH
oscGSHpred <- oscGSHpred %>%
  left_join(oscGSH_status, by = "Genus_species")
# SPL
oscSPLpred <- oscSPLpred %>%
  left_join(oscSPL_status, by = "Genus_species")
```

Pectoral undulation.

```{r}
# GSH
# Generate predicted data for smooth lines
undGSHpred <- logUnd %>%
  group_by(Genus_species) %>%
  reframe(logDW = seq(min(logDW), max(logDW), length.out = 100))
# Add model predicted values to data frame
undGSHpred$predictedGSH <- predict(undGSHmodel, newdata = undGSHpred)

# SPL
# Generate predicted data for smooth lines
undSPLpred <- logUnd %>%
  group_by(Genus_species) %>%
  reframe(logDW = seq(min(logDW), max(logDW), length.out = 100))
# Add model predicted values to data frame
undSPLpred$predictedSPL <- predict(undSPLmodel, newdata = undSPLpred)
```

Join the significance status to data

```{r}
# Actual data
# GSH
logUndGSH <- logUnd %>%
  left_join(undGSH_status, by = "Genus_species")
# SPL
logUndSPL <- logUnd %>%
  left_join(undSPL_status, by = "Genus_species")

# Predictions
# GSH
undGSHpred <- undGSHpred %>%
  left_join(undGSH_status, by = "Genus_species")
# SPL
undSPLpred <- undSPLpred %>%
  left_join(undSPL_status, by = "Genus_species")
```

# Plot results

Caudal propulsion.

```{r}
# Replace _ with " "
# Actual data
logCaudalGSH <- logCaudalGSH %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

logCaudalSPL <- logCaudalSPL %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

# GSH
# Predictions
caudalGSHpred <- caudalGSHpred %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

# SPL
# Predictions
caudalSPLpred <- caudalSPLpred %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
```

```{r}
# Plot GSH data with lines from model predictions
caudalGSHplot <- ggplot(data = logCaudalGSH, aes(x = logTL, y = logGSH_TL)) +
  geom_line(data = caudalGSHpred,
            aes(x = logTL, y = predictedGSH, group = Genus_species, 
                color = Significance),
            linewidth = 0.5) +
  geom_point(data = logCaudalGSH, aes(group = Genus_species, color = Significance)) +
  scale_color_manual(values = c("Significant" = "royalblue", 
                                "Not Significant" = "grey60")) +
  facet_wrap(~ Genus_species, scales = "free_x",
             ncol = 4) +
  scale_x_continuous(labels = function(x) round(10^x, 1)) +
  scale_y_continuous(labels = function(x) round(10^x, 1)) +
  labs(x = "Total length (cm)",
       y = "Relative gill slit height") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic"))

caudalGSHplot

ggsave("Results/Figures/caudalGSH.png", caudalGSHplot,
       width = 12, height = 9)

# Plot SPL data with lines from model predictions
caudalSPLplot <- ggplot(data = logCaudalSPL, aes(x = logTL, y = logSPL_TL)) +
  geom_line(data = caudalSPLpred,
            aes(x = logTL, y = predictedSPL, group = Genus_species, 
                color = Significance),
            linewidth = 0.5) +
  geom_point(data = logCaudalSPL, aes(group = Genus_species, color = Significance)) +
  scale_color_manual(values = c("Significant" = "royalblue", 
                                "Not Significant" = "grey60")) +
  facet_wrap(~ Genus_species, scales = "free_x",
             ncol = 4) +
  scale_x_continuous(labels = function(x) round(10^x, 1)) +
  scale_y_continuous(labels = function(x) round(10^x, 1)) +
  labs(x = "Total length (cm)",
       y = "Relative spiracle length") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic"))

caudalSPLplot

ggsave("Results/Figures/caudalSPL.png", caudalSPLplot,
       width = 12, height = 9)
```

Pectoral oscillation.

```{r}
# Replace _ with " "
# Actual data
logOscGSH <- logOscGSH %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

logOscSPL <- logOscSPL %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

# GSH
# Predictions
oscGSHpred <- oscGSHpred %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

# SPL
# Predictions
oscSPLpred <- oscSPLpred %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
```

```{r}
# Plot GSH data with lines from model predictions
oscGSHplot <- ggplot(data = logOscGSH, aes(x = logDW, y = logGSH_DW)) +
  geom_line(data = oscGSHpred,
            aes(x = logDW, y = predictedGSH, group = Genus_species, 
                color = Significance),
            linewidth = 0.5) +
  geom_point(data = logOscGSH, aes(group = Genus_species, color = Significance)) +
  scale_color_manual(values = c("Significant" = "royalblue", 
                                "Not Significant" = "grey60")) +
  facet_wrap(~ Genus_species, scales = "free_x",
             ncol = 2) +
  scale_x_continuous(labels = function(x) round(10^x, 1)) +
  scale_y_continuous(labels = function(x) round(10^x, 1)) +
  labs(x = "Disc Width (cm)",
       y = "Relative gill slit height") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic"))

oscGSHplot

ggsave("Results/Figures/oscGSH.png", oscGSHplot,
       width = 12, height = 9)

# Plot SPL data with lines from model predictions
oscSPLplot <- ggplot(data = logOscSPL, aes(x = logDW, y = logSPL_DW)) +
  geom_line(data = oscSPLpred,
            aes(x = logDW, y = predictedSPL, group = Genus_species, 
                color = Significance),
            linewidth = 0.5) +
  geom_point(data = logOscSPL, aes(group = Genus_species, color = Significance)) +
  scale_color_manual(values = c("Significant" = "royalblue", 
                                "Not Significant" = "grey60")) +
  facet_wrap(~ Genus_species, scales = "free_x",
             ncol = 2) +
  scale_x_continuous(labels = function(x) round(10^x, 1)) +
  scale_y_continuous(labels = function(x) round(10^x, 1)) +
  labs(x = "Disc Width (cm)",
       y = "Relative spiracle length") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic"))

oscSPLplot

ggsave("Results/Figures/oscSPL.png", oscSPLplot,
       width = 12, height = 9)
```

Pectoral undulation.

```{r}
# Replace _ with " "
# Actual data
logUndGSH <- logUndGSH %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

logUndSPL <- logUndSPL %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

# GSH
# Predictions
undGSHpred <- undGSHpred %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

# SPL
# Predictions
undSPLpred <- undSPLpred %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))
```

```{r}
# Plot GSH data with lines from model predictions
undGSHplot <- ggplot(data = logUndGSH, aes(x = logDW, y = logGSH_DW)) +
  geom_line(data = undGSHpred,
            aes(x = logDW, y = predictedGSH, group = Genus_species, 
                color = Significance),
            linewidth = 0.5) +
  geom_point(data = logUndGSH, aes(group = Genus_species, color = Significance)) +
  scale_color_manual(values = c("Significant" = "royalblue", 
                                "Not Significant" = "grey60")) +
  facet_wrap(~ Genus_species, scales = "free_x",
             ncol = 6) +
  scale_x_continuous(labels = function(x) round(10^x, 1)) +
  scale_y_continuous(labels = function(x) round(10^x, 1)) +
  labs(x = "Disc Width (cm)",
       y = "Relative gill slit height") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic"))

undGSHplot

ggsave("Results/Figures/undGSH.png", undGSHplot,
       width = 12, height = 9)

# Plot SPL data with lines from model predictions
undSPLplot <- ggplot(data = logUndSPL, aes(x = logDW, y = logSPL_DW)) +
  geom_line(data = undSPLpred,
            aes(x = logDW, y = predictedSPL, group = Genus_species, 
                color = Significance),
            linewidth = 0.5) +
  geom_point(data = logUndSPL, aes(group = Genus_species, color = Significance)) +
  scale_color_manual(values = c("Significant" = "royalblue", 
                                "Not Significant" = "grey60")) +
  facet_wrap(~ Genus_species, scales = "free_x",
             ncol = 6) +
  scale_x_continuous(labels = function(x) round(10^x, 1)) +
  scale_y_continuous(labels = function(x) round(10^x, 1)) +
  labs(x = "Disc width (cm)",
       y = "Relative spiracle length") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic"))

undSPLplot

ggsave("Results/Figures/undSPL.png", undSPLplot,
       width = 12, height = 9)
```
