---
title: "X_scalingAnalysis"
output: html_document
---

# 1. Load libraries

```{r}
# Load tidyverse
library(tidyverse)

# Load brms and tidybayes for analysis and interpretation
library(brms)
library(tidybayes)

# Load ape, geiger, and phytools for phylogenetic tree wrangling
library(ape)
library(geiger)
library(phytools)

# Load patchwork, cowplot, and scales for plotting
library(patchwork)
library(cowplot)
library(scales)
```

# 2. Load data

```{r}
# Load csv
rayData <- read.csv("Data/Data_Processed/RayDataTrimmed.csv")

# Load phylogenetic trees
rayTrees <- read.nexus("Data/Data_Processed/PrunedTrimmedTrees.nex")
```

# 3. Split data by body size metric (TL or DW)

```{r}
# % Total Length (TL) species
TLspecies <- rayData %>%
  filter(Order == "Rajiformes" | 
           Order == "Rhinopristiformes" | 
           Order == "Torpediniformes" | 
           Family == "Urolophidae" |
           Family == "Urotrygonidae")

# % Disc Width (DW) species
DWspecies <- rayData %>%
  filter(Family == "Aetobatidae" |
          Family == "Dasyatidae" |
          Family == "Gymnuridae" |
          Family == "Hexatrygonidae" |
          Family == "Mobulidae" |
          Family == "Myliobatidae" |
          Family == "Plesiobatidae" |
          Family == "Potamotrygonidae" |
          Family == "Rhinopteridae")
```

# 4. Calculate proportional size of spiracles and gills

```{r}
# TL
TLprop <- TLspecies %>%
  # Convert spiracles and gills to cm
  mutate(SPL_CM = SpiracleLength / 10,
         GSH_CM = GSavg / 10) %>%
  # Calculate proportions
  mutate(SPL_TL = SPL_CM / TotalLength_CM,
         GSH_TL = GSH_CM / TotalLength_CM) %>%
  # Drop rows with NAs in SPL or GSH
  drop_na(SPL_TL, GSH_TL) %>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()

# DW
DWprop <- DWspecies %>%
  # Convert spiracles and gills to cm
  mutate(SPL_CM = SpiracleLength / 10,
         GSH_CM = GSavg / 10) %>%
  # Calculate proportions
  mutate(SPL_DW = SPL_CM / DiscWidth_CM,
         GSH_DW = GSH_CM / DiscWidth_CM) %>%
  # Drop rows with NAs in SPL or GSH
  drop_na(SPL_DW, GSH_DW) %>%
  # Remove species with less than 4 individuals
  group_by(Genus_species) %>%
  filter(n() > 3) %>%
  ungroup()
```

# 5. Prepare phylogenetic trees

```{r}
# Set the seed for reproducibility
set.seed(123)
```

Trim trees to match each division of the dataset.

TL species

```{r}
# Sample out a single tree
TLtree <- sample(rayTrees, 1)[[1]]

# View which species are a mismatch between the tree and data
diffNamesTL <- name.check(TLtree, TLprop, TLprop$Genus_species)
# (should return a list of species in tree but not in data)

# Keep only tips that are present in the data
TLtree <- drop.tip(TLtree,
                   setdiff(TLtree$tip.label, TLprop$Genus_species))

# Check names again (should return "OK")
diffNamesTL <- name.check(TLtree, TLprop, TLprop$Genus_species)

# Keep only species present in the tree
TLprop <- TLprop[TLprop$Genus_species %in% TLtree$tip.label, ]
```

DW species

```{r}
# Sample out a single tree
DWtree <- sample(rayTrees, 1)[[1]]

# View which species are a mismatch between the tree and data
diffNamesDW <- name.check(DWtree, DWprop, DWprop$Genus_species)
# (should return a list of species in tree but not in data)

# Keep only tips that are present in the data
DWtree <- drop.tip(DWtree,
                   setdiff(DWtree$tip.label, DWprop$Genus_species))

# Check names again (should return "OK")
diffNamesDW <- name.check(DWtree, DWprop, DWprop$Genus_species)

# Keep only species present in the tree
DWprop <- DWprop[DWprop$Genus_species %in% DWtree$tip.label, ]
```

# 6. Analyze data with brms

## 6.1 TL species

Prepare data by logging x and y, and centering x

```{r}
# Log x (body size) and y (GSH and SPL)
TLlog <- TLprop %>%
  mutate(logGSH_TL = log10(GSH_TL),
         logSPL_TL = log10(SPL_TL),
         logTL = log10(TotalLength_CM))
```

Create and run brms models, and plot output

### 6.1.1 SPL

```{r}
# Create variance covariance matrix
TLmatrix <- ape::vcv(TLtree)

# Scale TL (predictor (x))
TLscaled <- TLlog %>%
  # "Scale" by centering only (since testing isometry)
  mutate(scaleTL = scale(logTL, center = TRUE, scale = FALSE))

# Build and run model
TL_SPL <- brm(logSPL_TL ~ scaleTL +
                (1 + scaleTL | gr(Genus_species, cov = TLmatrix)),
          data = TLscaled,
          data2 = list(TLmatrix = TLmatrix),
          family = gaussian,
          warmup = 3000, iter = 6000,
          cores = 2, control = list(adapt_delta = 0.95),
          save_pars = save_pars(all = TRUE))

summary(TL_SPL)

# Save brms object
saveRDS(TL_SPL, "Results/brmsOutputs/TL_SPL.rds")
```

```{r}
# Optional: load brms object if revisiting script
TL_SPL <- readRDS("Results/brmsOutputs/TL_SPL.rds")
```

Extract model outputs

```{r}
TL_SPL_slopes <- TL_SPL %>%
  # Get "global" posterior draws
  spread_draws(b_scaleTL,
    # Get species level posterior draws
    r_Genus_species[Genus_species, term]) %>%
  # Filter for slopes (remove Intercept)
  filter(term == "scaleTL") %>%
  # Calculate species' "true" slope (global slope + slope relative to "global" slope)
  mutate(slope = b_scaleTL + r_Genus_species)

# Summarize by species
TL_SPL_sum <- TL_SPL_slopes %>%
  median_qi(slope, .width = 0.95) %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "),
         # Flag species that deviate from expectations (0)
         significant = (.lower >=0 | .upper <= 0))
```

Create coefficient plot

```{r}
TL_SPL_coef <- ggplot(TL_SPL_sum,
       aes(x = slope, y = reorder(Genus_species, slope), 
           color = significant)) +
  geom_vline(xintercept = 0, color = "grey50") +
  geom_errorbar(aes(xmin = .lower, xmax = .upper),
                width = 0) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = NULL,
        y = NULL) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 8, face = "italic"),
        legend.position = "none")

ggsave("Results/Figures/TL_SPL_coef .png", TL_SPL_coef ,
       width = 8, height = 10)
```

### 6.1.2 GSH

```{r}
# Build and run model
TL_GSH <- brm(logGSH_TL ~ scaleTL +
                     (1 + scaleTL | gr(Genus_species, cov = TLmatrix)),
          data = TLscaled,
          data2 = list(TLmatrix = TLmatrix),
          family = gaussian,
          warmup = 3000, iter = 6000,
          cores = 2, control = list(adapt_delta = 0.95),
          save_pars = save_pars(all = TRUE))

summary(TL_GSH)

# Save brms object
saveRDS(TL_GSH, "Results/brmsOutputs/TL_GSH.rds")
```

```{r}
# Optional: load brms object if revisiting script
TL_GSH <- readRDS("Results/brmsOutputs/TL_GSH.rds")
```

Extract model outputs

```{r}
TL_GSH_slopes <- TL_GSH %>%
  # Get "global" posterior draws
  spread_draws(b_scaleTL,
    # Get species level posterior draws
    r_Genus_species[Genus_species, term]) %>%
  # Filter for slopes (remove Intercept)
  filter(term == "scaleTL") %>%
  # Calculate species' "true" slope (global slope + slope relative to "global" slope)
  mutate(slope = b_scaleTL + r_Genus_species)

# Summarize by species
TL_GSH_sum <- TL_GSH_slopes %>%
  median_qi(slope, .width = 0.95) %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "),
         # Flag species that deviate from expectations
         significant = (.lower >=0 | .upper <= 0))
```

Create coefficient plot

```{r}
TL_GSH_coef <- ggplot(TL_GSH_sum,
       aes(x = slope, y = reorder(Genus_species, slope),
           color = significant)) +
  geom_vline(xintercept = 0, color = "grey50") +
  geom_errorbar(aes(xmin = .lower, xmax = .upper),
                width = 0) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = NULL,
       y = NULL) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 8, face = "italic"),
        legend.position = "none")

ggsave("Results/Figures/TL_GSH_coef.png", TL_GSH_coef,
       width = 8, height = 10)
```

## 6.2 DW species

Prepare data by logging x and y, and centering x

```{r}
# Log x (body size) and y (GSH and SPL)
DWlog <- DWprop %>%
  mutate(logGSH_DW = log10(GSH_DW),
         logSPL_DW = log10(SPL_DW),
         logDW = log10(DiscWidth_CM))
```

Create and run brms models

### 6.2.1 SPL

```{r}
# Create variance covariance matrix
DWmatrix <- ape::vcv(DWtree)

# Scale DW (predictor (x))
DWscaled <- DWlog %>%
  # "Scale" by centering only (since testing isometry)
  mutate(scaleDW = scale(logDW, center = TRUE, scale = FALSE))

# Build and run model
DW_SPL <- brm(logSPL_DW ~ scaleDW +
                     (1 + scaleDW | gr(Genus_species, cov = DWmatrix)),
          data = DWscaled,
          data2 = list(DWmatrix = DWmatrix),
          family = gaussian,
          warmup = 3000, iter = 6000,
          cores = 2, control = list(adapt_delta = 0.95),
          save_pars = save_pars(all = TRUE))

summary(DW_SPL)

# Save brms object
saveRDS(DW_SPL, "Results/brmsOutputs/DW_SPL.rds")
```

```{r}
# Optional: load brms object if revisiting script
DW_SPL <- readRDS("Results/brmsOutputs/DW_SPL.rds")
```

Extract model outputs

```{r}
DW_SPL_slopes <- DW_SPL %>%
  # Get "global" posterior draws
  spread_draws(b_scaleDW,
    # Get species level posterior draws
    r_Genus_species[Genus_species, term]) %>%
  # Filter for slopes (remove Intercept)
  filter(term == "scaleDW") %>%
  # Calculate species' "true" slope (global slope + slope relative to "global" slope)
  mutate(slope = b_scaleDW + r_Genus_species)

# Summarize by species
DW_SPL_sum <- DW_SPL_slopes %>%
  median_qi(slope, .width = 0.95) %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "),
         # Flag species that deviate from expectations
         significant = (.lower >=0 | .upper <= 0))
```

Plot 

```{r}
DW_SPL_coef <- ggplot(DW_SPL_sum,
                     aes(x = slope, y = reorder(Genus_species, slope),
                         color = significant)) +
  geom_vline(xintercept = 0, color = "grey50") +
  geom_errorbar(aes(xmin = .lower, xmax = .upper),
                width = 0) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = NULL,
        y = NULL) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 8, face = "italic"),
        legend.position = "none")

ggsave("Results/Figures/DW_SPL_coef.png", DW_SPL_coef,
       width = 8, height = 10)
```

### 6.2.2 GSH

```{r}
# Build and run model
DW_GSH <- brm(logGSH_DW ~ scaleDW +
                     (1 + scaleDW | gr(Genus_species, cov = DWmatrix)),
          data = DWscaled,
          data2 = list(DWmatrix = DWmatrix),
          family = gaussian,
          warmup = 3000, iter = 6000,
          cores = 2, control = list(adapt_delta = 0.95),
          save_pars = save_pars(all = TRUE))

summary(DW_GSH)

# Save brms object
saveRDS(DW_GSH, "Results/brmsOutputs/DW_GSH.rds")
```

```{r}
# Optional: load brms object if revisiting script
DW_GSH <- readRDS("Results/brmsOutputs/DW_GSH.rds")
```

Extract model outputs

```{r}
DW_GSH_slopes <- DW_GSH %>%
  # Get "global" posterior draws
  spread_draws(b_scaleDW,
    # Get species level posterior draws
    r_Genus_species[Genus_species, term]) %>%
  # Filter for slopes (remove Intercept)
  filter(term == "scaleDW") %>%
  # Calculate species' "true" slope (global slope + slope relative to "global" slope)
  mutate(slope = b_scaleDW + r_Genus_species)

# Summarize by species
DW_GSH_sum <- DW_GSH_slopes %>%
  median_qi(slope, .width = 0.95) %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "),
         # Flag species that deviate from expectations
         significant = (.lower >=0 | .upper <= 0))
```

Create coefficient plot

```{r}
DW_GSH_coef <- ggplot(DW_GSH_sum,
                     aes(x = slope, y = reorder(Genus_species, slope),
           color = significant)) +
  geom_vline(xintercept = 0, color = "grey50") +
  geom_errorbar(aes(xmin = .lower, xmax = .upper),
                width = 0) +
  geom_point(size = 2.5) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = NULL,
       y = NULL) +
  theme_classic() +
  theme(axis.text.y = element_text(size = 8, face = "italic"),
        legend.position = "none")

ggsave("Results/Figures/DW_GSH_coef.png", DW_GSH_coef,
       width = 8, height = 10)
```

# Supplementary Figures

Plot individual species original data with brms model fit

TL species

SPL

```{r}
# Extract species significance from model summary
TL_SPL_sig <- TL_SPL_sum %>%
  select(Genus_species, significant)

# Join significance status
TLnamed <- TLscaled %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

TLnamed <- TLnamed %>%
  # Left join significance
  left_join(TL_SPL_sig, by = "Genus_species")
```

```{r}
# Make a prediction grid
TL_SPL_pred <- TLscaled %>%
  group_by(Genus_species) %>%
  summarise(
    min_x = min(scaleTL, na.rm = TRUE),
    max_x = max(scaleTL, na.rm = TRUE),
    .groups = "drop") %>%
  crossing(scaleTL = seq(min(TLscaled$scaleTL, na.rm = TRUE),
                         max(TLscaled$scaleTL, na.rm = TRUE),
                         length.out = 100)) %>%
  filter(scaleTL >= min_x, scaleTL <= max_x) %>%
  select(Genus_species, scaleTL)

# Draw from the posterior
TL_SPL_preds <- TL_SPL %>%
  add_epred_draws(newdata = TL_SPL_pred,
                  ndraws = 100)

# Summarize
TL_SPL_preds_sum <- TL_SPL_preds %>%
  group_by(Genus_species, scaleTL) %>%
  median_qi(.epred, .width = 0.95) %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " ")) %>%
  # Left join significance
  left_join(TL_SPL_sig, by = "Genus_species")
```

```{r}
TL_SPL_species <- ggplot(TLnamed, aes(x = scaleTL, y = logSPL_TL, 
                                      color = significant)) +
  geom_line(data = TL_SPL_preds_sum, aes(x = scaleTL, y = .epred,
                                         color = significant), linewidth = 0.5) +
  geom_point() +
  facet_wrap(~ Genus_species, scales = "free_x", ncol = 5) +
  scale_x_continuous(labels = function(x) round(10^x, 1),
                     breaks = function(x) seq(x[1], x[2], length.out = 3)) +
  scale_y_continuous(labels = function(y) round(10^y, 2)) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = "Total Length",
       y = "Relative Spiracle Length") +
  theme_classic() +
  theme(axis.text = element_text(size = 6),
        # Set facet strip aesthetics
        strip.text = element_text(face = "italic", size = 8),
        strip.background = element_blank(),
        panel.spacing.x = unit(1, "lines"),
        legend.position = "none")

ggsave("Results/Figures/TL_SPL.png", TL_SPL_species,
       width = 8.5, height = 11)
```

GSH

```{r}
# Extract species significance from model summary
TL_GSH_sig <- TL_GSH_sum %>%
  select(Genus_species, significant)

# Join significance status
TLnamed <- TLscaled %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

TLnamed <- TLnamed %>%
  # Left join significance
  left_join(TL_GSH_sig, by = "Genus_species")
```

```{r}
# Make a prediction grid
TL_GSH_pred <- TLscaled %>%
  group_by(Genus_species) %>%
  summarise(
    min_x = min(scaleTL, na.rm = TRUE),
    max_x = max(scaleTL, na.rm = TRUE),
    .groups = "drop") %>%
  crossing(scaleTL = seq(min(TLscaled$scaleTL, na.rm = TRUE),
                         max(TLscaled$scaleTL, na.rm = TRUE),
                         length.out = 100)) %>%
  filter(scaleTL >= min_x, scaleTL <= max_x) %>%
  select(Genus_species, scaleTL)

# Draw from the posterior
TL_GSH_preds <- TL_GSH %>%
  add_epred_draws(newdata = TL_GSH_pred,
                  ndraws = 100)

# Summarize
TL_GSH_preds_sum <- TL_GSH_preds %>%
  group_by(Genus_species, scaleTL) %>%
  median_qi(.epred, .width = 0.95) %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " ")) %>%
  # Left join significance
  left_join(TL_GSH_sig, by = "Genus_species")
```

```{r}
TL_GSH_species <- ggplot(TLnamed, aes(x = scaleTL, y = logGSH_TL, 
                                      color = significant)) +
  geom_line(data = TL_GSH_preds_sum, aes(x = scaleTL, y = .epred,
                                         color = significant), linewidth = 0.5) +
  geom_point() +
  facet_wrap(~ Genus_species, scales = "free_x", ncol = 5) +
  scale_x_continuous(labels = function(x) round(10^x, 1),
                     breaks = function(x) seq(x[1], x[2], length.out = 3)) +
  scale_y_continuous(labels = function(y) round(10^y, 2)) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = "Total Length",
       y = "Relative Gill Slit Height") +
  theme_classic() +
  theme(axis.text = element_text(size = 6),
        # Set facet strip aesthetics
        strip.text = element_text(face = "italic", size = 8),
        strip.background = element_blank(),
        panel.spacing.x = unit(1, "lines"),
        legend.position = "none")

ggsave("Results/Figures/TL_GSH.png", TL_GSH_species,
       width = 8.5, height = 11)
```

DW species

SPL

```{r}
# Extract species significance from model summary
DW_SPL_sig <- DW_SPL_sum %>%
  select(Genus_species, significant)

# Join significance status
DWnamed <- DWscaled %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

DWnamed <- DWnamed %>%
  # Left join significance
  left_join(DW_SPL_sig, by = "Genus_species")
```

```{r}
# Make a prediction grid
DW_SPL_pred <- DWscaled %>%
  group_by(Genus_species) %>%
  summarise(
    min_x = min(scaleDW, na.rm = TRUE),
    max_x = max(scaleDW, na.rm = TRUE),
    .groups = "drop") %>%
  crossing(scaleDW = seq(min(DWscaled$scaleDW, na.rm = TRUE),
                         max(DWscaled$scaleDW, na.rm = TRUE),
                         length.out = 100)) %>%
  filter(scaleDW >= min_x, scaleDW <= max_x) %>%
  select(Genus_species, scaleDW)

# Draw from the posterior
DW_SPL_preds <- DW_SPL %>%
  add_epred_draws(newdata = DW_SPL_pred,
                  ndraws = 100)

# Summarize
DW_SPL_preds_sum <- DW_SPL_preds %>%
  group_by(Genus_species, scaleDW) %>%
  median_qi(.epred, .width = 0.95) %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " ")) %>%
  # Left join significance
  left_join(DW_SPL_sig, by = "Genus_species")
```

```{r}
DW_SPL_species <- ggplot(DWnamed, aes(x = scaleDW, y = logSPL_DW, 
                                      color = significant)) +
  geom_line(data = DW_SPL_preds_sum, aes(x = scaleDW, y = .epred,
                                         color = significant), linewidth = 0.5) +
  geom_point() +
  facet_wrap(~ Genus_species, scales = "free_x", ncol = 5) +
  scale_x_continuous(labels = function(x) round(10^x, 1),
                     breaks = function(x) seq(x[1], x[2], length.out = 3)) +
  scale_y_continuous(labels = function(y) round(10^y, 2)) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = "Disc Width",
       y = "Relative Spiracle Length") +
  theme_classic() +
  theme(axis.text = element_text(size = 6),
        # Set facet strip aesthetics
        strip.text = element_text(face = "italic", size = 8),
        strip.background = element_blank(),
        panel.spacing.x = unit(1, "lines"),
        legend.position = "none")

ggsave("Results/Figures/DW_SPL.png", DW_SPL_species,
       width = 8.5, height = 11)
```

GSH

```{r}
# Extract species significance from model summary
DW_GSH_sig <- DW_GSH_sum %>%
  select(Genus_species, significant)

# Join significance status
DWnamed <- DWscaled %>%
  # Replace _ with "" in species names
  mutate(Genus_species = str_replace_all(Genus_species, "_", " "))

DWnamed <- DWnamed %>%
  # Left join significance
  left_join(DW_GSH_sig, by = "Genus_species")
```

```{r}
# Make a prediction grid
DW_GSH_pred <- DWscaled %>%
  group_by(Genus_species) %>%
  summarise(
    min_x = min(scaleDW, na.rm = TRUE),
    max_x = max(scaleDW, na.rm = TRUE),
    .groups = "drop") %>%
  crossing(scaleDW = seq(min(DWscaled$scaleDW, na.rm = TRUE),
                         max(DWscaled$scaleDW, na.rm = TRUE),
                         length.out = 100)) %>%
  filter(scaleDW >= min_x, scaleDW <= max_x) %>%
  select(Genus_species, scaleDW)

# Draw from the posterior
DW_GSH_preds <- DW_GSH %>%
  add_epred_draws(newdata = DW_GSH_pred,
                  ndraws = 100)

# Summarize
DW_GSH_preds_sum <- DW_GSH_preds %>%
  group_by(Genus_species, scaleDW) %>%
  median_qi(.epred, .width = 0.95) %>%
  mutate(Genus_species = str_replace_all(Genus_species, "_", " ")) %>%
  # Left join significance
  left_join(DW_GSH_sig, by = "Genus_species")
```

```{r}
DW_GSH_species <- ggplot(DWnamed, aes(x = scaleDW, y = logGSH_DW, 
                                      color = significant)) +
  geom_line(data = DW_GSH_preds_sum, aes(x = scaleDW, y = .epred,
                                         color = significant), linewidth = 0.5) +
  geom_point() +
  facet_wrap(~ Genus_species, scales = "free_x", ncol = 5) +
  scale_x_continuous(labels = function(x) round(10^x, 1),
                     breaks = function(x) seq(x[1], x[2], length.out = 3)) +
  scale_y_continuous(labels = function(y) round(10^y, 2)) +
  scale_color_manual(values = c("TRUE" = "darkslategray3", 
                                "FALSE" = "darkslategray")) +
  labs(x = "Disc Width",
       y = "Relative Gill Slit Height") +
  theme_classic() +
  theme(axis.text = element_text(size = 6),
        # Set facet strip aesthetics
        strip.text = element_text(face = "italic", size = 8),
        strip.background = element_blank(),
        panel.spacing.x = unit(1, "lines"),
        legend.position = "none")

ggsave("Results/Figures/DW_GSH.png", DW_GSH_species,
       width = 8.5, height = 11)
```

```{r}
# Determine effect size
TL_SPL_draws <- as_draws_df(TL_SPL)
# Calculate effect size
TL_SPL_draws <- 
```

